### 2024-02-16 papers/ISMM/FlexPointer/paper.tex

%%
%% This is file `sample-acmsmall-submission.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall-submission')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall-submission.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{acmart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{acmart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[acmsmall,screen,review]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}

%%
%% These commands are for a JOURNAL article.
\acmJournal{JACM}
\acmVolume{37}
\acmNumber{4}
\acmArticle{111}
\acmMonth{8}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{FAT-Pointer based range addresses}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Akilan Selvacoumar}
% \authornote{Both authors contributed equally to this research.}
\email{as251@hw.ac.uk}
\orcid{1234-5678-9012}
% \author{G.K.M. Tobin}
% \authornotemark[1]
% \email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Heriot Watt University}
  % \streetaddress{P.O. Box 1212}
  % \city{Dublin}
  % \state{Ohio}
  \country{UK}
  % \postcode{43017-6221}
}

% \author{Lars Th{\o}rv{\"a}ld}
% \affiliation{%
%   \institution{The Th{\o}rv{\"a}ld Group}
%   \streetaddress{1 Th{\o}rv{\"a}ld Circle}
%   \city{Hekla}
%   \country{Iceland}}
% \email{larst@affiliation.org}

% \author{Valerie B\'eranger}
% \affiliation{%
%   \institution{Inria Paris-Rocquencourt}
%   \city{Rocquencourt}
%   \country{France}
% }

% \author{Aparna Patel}
% \affiliation{%
%  \institution{Rajiv Gandhi University}
%  \streetaddress{Rono-Hills}
%  \city{Doimukh}
%  \state{Arunachal Pradesh}
%  \country{India}}

% \author{Huifen Chan}
% \affiliation{%
%   \institution{Tsinghua University}
%   \streetaddress{30 Shuangqing Rd}
%   \city{Haidian Qu}
%   \state{Beijing Shi}
%   \country{China}}

% \author{Charles Palmer}
% \affiliation{%
%   \institution{Palmer Research Laboratories}
%   \streetaddress{8600 Datapoint Drive}
%   \city{San Antonio}
%   \state{Texas}
%   \country{USA}
%   \postcode{78229}}
% \email{cpalmer@prl.com}

% \author{John Smith}
% \affiliation{%
%   \institution{The Th{\o}rv{\"a}ld Group}
%   \streetaddress{1 Th{\o}rv{\"a}ld Circle}
%   \city{Hekla}
%   \country{Iceland}}
% \email{jsmith@affiliation.org}

% \author{Julius P. Kumquat}
% \affiliation{%
%   \institution{The Kumquat Consortium}
%   \city{New York}
%   \country{USA}}
% \email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
% \renewcommand{\shortauthors}{Trovato et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  The gap between application workloads and capacity of TLB is on the 
  rise. Previous work exploits this by physically contiguous 
  memory. Capability-based addressing in the CHERI architecture is 
  designed to improve hardware-level system security.
  These security mechanisms designed in place can also 
  behave as accelerators to standard user-space memory allocators. 
  The property of CHERI which is to use FAT-Pointers to store
  the upper and lower bounds can also be represented as ranges of 
  memory addresses which are physically contiguous. 
  <Talking about the results>.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>00000000.0000000.0000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
  Your, Paper}

\received{20 February 2007}
\received[revised]{12 March 2009}
\received[accepted]{5 June 2009}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-anonymous initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\texttt{acmsmall}}: The default journal template style.
\item {\texttt{acmlarge}}: Used by JOCCH and TAP.
\item {\texttt{acmtog}}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\texttt{sigconf}}: The default proceedings template style.
\item{\texttt{sigchi}}: Used for SIGCHI conference articles.
\item{\texttt{sigplan}}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\texttt{anonymous,review}}: Suitable for a ``double-anonymous''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \texttt{\acmSubmissionID} command to print the
  submission's unique ID on each page of the work.
\item{\texttt{authorversion}}: Produces a version of the work suitable
  for posting by the author.
\item{\texttt{screen}}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[acmsmall,screen,review]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification.  As an exception, multiple authors may share one
affiliation. Authors' names should not be abbreviated; use full first
names wherever possible. Include authors' e-mail addresses whenever
possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

Always use midrule to separate table header rows from data rows, and
use it only for this purpose. This enables assistive technologies to
recognise table headers and support their users in navigating tables
more easily.

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
% \begin{figure}[h]
%   \centering
%   \includegraphics[width=\linewidth]{sample-franklin}
%   \caption{1907 Franklin Model D roadster. Photograph by Harris \&
%     Ewing, Inc. [Public domain], via Wikimedia
%     Commons. (\url{https://goo.gl/VLCRBB}).}
%   \Description{A woman and a girl in white dresses sit in an open car.}
% \end{figure}

Your figures should contain a caption which describes the figure to
the reader.

Figure captions are placed {\itshape below} the figure.

Every figure should also have a figure description unless it is purely
decorative. These descriptions convey what’s in the image to someone
who cannot see it. They are also used by search engine crawlers for
indexing images, and when images cannot be loaded.

A figure description must be unformatted plain text less than 2000
characters long (including spaces).  {\bfseries Figure descriptions
  should not repeat the figure caption – their purpose is to capture
  important information that is not already provided in the caption or
  the main text of the paper.} For figures that convey important and
complex new information, a short text description may not be
adequate. More complex alternative descriptions can be placed in an
appendix and referenced in a short figure description. For example,
provide a data table capturing the information in a bar chart, or a
structured list representing a graph.  For additional information
regarding how best to write figure descriptions and why doing this is
so important, please see
\url{https://www.acm.org/publications/taps/describing-figures/}.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before the command
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, a couple of articles in a proceedings (of a
  conference, symposium, workshop for example) (paginated proceedings
  article) \cite{Andler79, Hagerup1993}, a proceedings article with
  all possible elements \cite{Smith10}, an example of an enumerated
  proceedings article \cite{VanGundy07}, an informally published work
  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
  master's thesis: \cite{anisi03}, an online document / world wide web
  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
  Artifacts: \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{Multi-language papers}

Papers may be written in languages other than English or include
titles, subtitles, keywords and abstracts in different languages (as a
rule, a paper in a language other than English should include an
English title and an English abstract).  Use \verb|language=...| for
every language used in the paper.  The last language indicated is the
main language of the paper.  For example, a French paper with
additional titles and abstracts in English and German may start with
the following command
\begin{verbatim}
\documentclass[sigconf, language=english, language=german,
               language=french]{acmart}
\end{verbatim}

The title, subtitle, keywords and abstract will be typeset in the main
language of the paper.  The commands \verb|\translatedXXX|, \verb|XXX|
begin title, subtitle and keywords, can be used to set these elements
in the other languages.  The environment \verb|translatedabstract| is
used to set the translation of the abstract.  These commands and
environment have a mandatory first argument: the language of the
second argument.  See \verb|sample-sigconf-i13n.tex| file for examples
of their usage.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{description}
\item[\texttt{sidebar}:]  Place formatted text in the margin.
\item[\texttt{marginfigure}:] Place a figure in the margin.
\item[\texttt{margintable}:] Place a table in the margin.
\end{description}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-acmsmall-submission.tex'.

### 2024-02-16 example/TestBenchmarks/Kmeans.c
added kmeans with contigous allocation

@@ -1,0 +1,372 @@
+
+/* Copyright (c) 2007-2009, Stanford University
+* All rights reserved.
+*
+* Redistribution and use in source and binary forms, with or without
+* modification, are permitted provided that the following conditions are met:
+*     * Redistributions of source code must retain the above copyright
+*       notice, this list of conditions and the following disclaimer.
+*     * Redistributions in binary form must reproduce the above copyright
+*       notice, this list of conditions and the following disclaimer in the
+*       documentation and/or other materials provided with the distribution.
+*     * Neither the name of Stanford University nor the names of its 
+*       contributors may be used to endorse or promote products derived from 
+*       this software without specific prior written permission.
+*
+* THIS SOFTWARE IS PROVIDED BY STANFORD UNIVERSITY ``AS IS'' AND ANY
+* EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+* WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
+* DISCLAIMED. IN NO EVENT SHALL STANFORD UNIVERSITY BE LIABLE FOR ANY
+* DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES
+* (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
+* LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
+* ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+* (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+* SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+*/ 
+
+#include <stdio.h>
+#include <strings.h>
+#include <string.h>
+#include <stddef.h>
+#include <stdlib.h>
+#include <unistd.h>
+#include <assert.h>
+#include <string.h>
+#include <math.h>
+#include <pthread.h>
+
+#include "stddefines.h"
+
+#include "coz.h"
+
+// #include "prof.h"
+
[…]

### 2024-02-23 example/TestBenchmarks/Kmeans.c
testing parallel program

@@ -248,7 +248,7 @@ void *calc_means(void *arg)
          }
       }
    }
-   FREE(sum);
+   free(sum);
    return (void *)0;
 }
 
@@ -266,23 +266,23 @@ int main(int argc, char **argv)
 
    // PROF_START();
    
-   points = (int **)MALLOC(sizeof(int *) * num_points);
+   points = (int **)malloc(sizeof(int *) * num_points);
    for (i=0; i<num_points; i++) 
    {
-      points[i] = (int *)MALLOC(sizeof(int) * dim);
+      points[i] = (int *)malloc(sizeof(int) * dim);
    }
    dprintf("Generating points\n");
    generate_points(points, num_points);
    
-   means = (int **)MALLOC(sizeof(int *) * num_means);
+   means = (int **)malloc(sizeof(int *) * num_means);
    for (i=0; i<num_means; i++) 
    {
-      means[i] = (int *)MALLOC(sizeof(int) * dim);
+      means[i] = (int *)malloc(sizeof(int) * dim);
    }
    dprintf("Generating means\n");
    generate_points(means, num_means);
  
-   clusters = (int *)MALLOC(sizeof(int) * num_points);
+   clusters = (int *)malloc(sizeof(int) * num_points);
    memset(clusters, -1, sizeof(int) * num_points);
    
    
@@ -290,7 +290,7 @@ int main(int argc, char **argv)
    pthread_attr_setscope(&attr, PTHREAD_SCOPE_SYSTEM);
    CHECK_ERROR((num_procs = sysconf(_SC_NPROCESSORS_ONLN)) <= 0);
       
-   CHECK_ERROR( (pid = (pthread_t *)MALLOC(sizeof(pthread_t) * num_procs)) == NULL);
+   CHECK_ERROR( (pid = (pthread_t *)malloc(sizeof(pthread_t) * num_procs)) == NULL);
    
    modified = true; 
    
@@ -309,7 +309,7 @@ int main(int argc, char **argv)
       num_threads = 0;
       
       while (curr_point < num_points) {
-         CHECK_ERROR((arg = (thread_arg *)MALLOC(sizeof(thread_arg))) == NULL);
+         CHECK_ERROR((arg = (thread_arg *)malloc(sizeof(thread_arg))) == NULL);
          arg->start_idx = curr_point;
          arg->num_pts = num_per_thread;
          if (excess > 0) {
@@ -331,9 +331,9 @@ int main(int argc, char **argv)
       curr_point = 0;
[…]

### 2024-02-23 example/TestBenchmarks/Kmeans.c
added malloc defaults

@@ -248,7 +248,7 @@ void *calc_means(void *arg)
          }
       }
    }
-   free(sum);
+   FREE(sum);
    return (void *)0;
 }
 
@@ -266,23 +266,23 @@ int main(int argc, char **argv)
 
    // PROF_START();
    
-   points = (int **)malloc(sizeof(int *) * num_points);
+   points = (int **)MALLOC(sizeof(int *) * num_points);
    for (i=0; i<num_points; i++) 
    {
-      points[i] = (int *)malloc(sizeof(int) * dim);
+      points[i] = (int *)MALLOC(sizeof(int) * dim);
    }
    dprintf("Generating points\n");
    generate_points(points, num_points);
    
-   means = (int **)malloc(sizeof(int *) * num_means);
+   means = (int **)MALLOC(sizeof(int *) * num_means);
    for (i=0; i<num_means; i++) 
    {
-      means[i] = (int *)malloc(sizeof(int) * dim);
+      means[i] = (int *)MALLOC(sizeof(int) * dim);
    }
    dprintf("Generating means\n");
    generate_points(means, num_means);
  
-   clusters = (int *)malloc(sizeof(int) * num_points);
+   clusters = (int *)MALLOC(sizeof(int) * num_points);
    memset(clusters, -1, sizeof(int) * num_points);
    
    
@@ -290,7 +290,7 @@ int main(int argc, char **argv)
    pthread_attr_setscope(&attr, PTHREAD_SCOPE_SYSTEM);
    CHECK_ERROR((num_procs = sysconf(_SC_NPROCESSORS_ONLN)) <= 0);
       
-   CHECK_ERROR( (pid = (pthread_t *)malloc(sizeof(pthread_t) * num_procs)) == NULL);
+   CHECK_ERROR( (pid = (pthread_t *)MALLOC(sizeof(pthread_t) * num_procs)) == NULL);
    
    modified = true; 
    
@@ -309,7 +309,7 @@ int main(int argc, char **argv)
       num_threads = 0;
       
       while (curr_point < num_points) {
-         CHECK_ERROR((arg = (thread_arg *)malloc(sizeof(thread_arg))) == NULL);
+         CHECK_ERROR((arg = (thread_arg *)MALLOC(sizeof(thread_arg))) == NULL);
          arg->start_idx = curr_point;
          arg->num_pts = num_per_thread;
          if (excess > 0) {
@@ -331,9 +331,9 @@ int main(int argc, char **argv)
       curr_point = 0;
[…]

### 2024-02-23 example/TestBenchmarks/stddefines.h
added contig malloc

@@ -44,7 +44,7 @@
 
 //#define TIMING
 
-// #define FILENAME "/dev/contigmem"
+#define FILENAME "/dev/contigmem"
 
 /* Debug printf */
 #define dprintf(...) fprintf(stdout, __VA_ARGS__)
@@ -64,35 +64,35 @@ static inline void *MALLOC(size_t size)
 //    return temp;
 
 // Ensuring malloc this is mmap and phyiscally contigous
-   //  int fd = open
-	// (FILENAME, O_RDWR | O_CREAT, 0600);
-	// if (fd < 0) {
-	// 	perror("open");
-	// 	exit(EXIT_FAILURE);
-	// }
+    int fd = open
+	(FILENAME, O_RDWR | O_CREAT, 0600);
+	if (fd < 0) {
+		perror("open");
+		exit(EXIT_FAILURE);
+	}
 
 	off_t offset = 0; // offset to seek to.
 
-	// if (ftruncate(fd, size) < 0) {
-	// 	perror("ftruncate");
-	// 	close(fd);
-	// 	exit(EXIT_FAILURE);
-	// }
+	if (ftruncate(fd, size) < 0) {
+		perror("ftruncate");
+		close(fd);
+		exit(EXIT_FAILURE);
+	}
 
-	// int *ptr = mmap(NULL, size,
-	//                          PROT_READ | PROT_WRITE, MAP_SHARED,
-	//                          -1, offset);
-	// if(ptr == MAP_FAILED)
-	// {
-	// 	perror("mmap");
-	// 	exit(EXIT_FAILURE);
-	// }
+	int *ptr = mmap(NULL, size,
+	                         PROT_READ | PROT_WRITE, MAP_SHARED,
+	                         -1, offset);
+	if(ptr == MAP_FAILED)
+	{
+		perror("mmap");
+		exit(EXIT_FAILURE);
+	}
 
-   //  *ptr = size;
+    *ptr = size;
 
-   //  return &ptr[1];
-   void *ptr = malloc(size);
-   return ptr;
+    return ptr[1];
+   // void *ptr = malloc(size);
+   // return ptr;
 }
 
 static inline void *CALLOC(size_t num, size_t size)

### 2024-02-23 example/TestBenchmarks/stddefines.h
debug in address space security faullt

@@ -90,7 +90,7 @@ static inline void *MALLOC(size_t size)
 
     *ptr = size;
 
-    return ptr[1];
+    return ptr;
    // void *ptr = malloc(size);
    // return ptr;
 }
@@ -118,16 +118,16 @@ static inline char *GETENV(char *envstr)
 
 static inline void *FREE(void *ptr)
 {
-   //  int *pt = ptr;
-   //  size_t size;
-   //  --pt;
-   //  size = *pt;
-   //  if(munmap(pt, size) == -1)
-	// {
-	// 	perror("munmap");
-	// 	exit(EXIT_FAILURE);
-	// }
-   free(ptr);
+    int *pt = ptr;
+    size_t size;
+    --pt;
+    size = *pt;
+    if(munmap(pt, size) == -1)
+	{
+		perror("munmap");
+		exit(EXIT_FAILURE);
+	}
+   // free(ptr);
 }
 
 #define GET_TIME(start, end, duration)                                     \

### 2024-02-25 papers/ISMM/FlexPointer/paper.tex
added FlexPointer section

@@
 %%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>00000000.0000000.0000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>00000000.00000000.00000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>00000000.00000000.00000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>00000000.00000000.00000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
+% \begin{CCSXML}
+% <ccs2012>
+%  <concept>
+%   <concept_id>00000000.0000000.0000000</concept_id>
+%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+%   <concept_significance>500</concept_significance>
+%  </concept>
+%  <concept>
+%   <concept_id>00000000.00000000.00000000</concept_id>
+%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+%   <concept_significance>300</concept_significance>
+%  </concept>
+%  <concept>
+%   <concept_id>00000000.00000000.00000000</concept_id>
+%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+%   <concept_significance>100</concept_significance>
+%  </concept>
+%  <concept>
+%   <concept_id>00000000.00000000.00000000</concept_id>
+%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+%   <concept_significance>100</concept_significance>
+%  </concept>
+% </ccs2012>
+% \end{CCSXML}
 
@@
 
-\section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
+\section{Related work}
+\subsection{Huge Pages}
+This is used to map a very large region of memory to a 
+single entry. This small/large region of memory is physically
+contiguous. Most implementations of huge pages are size
+aligned, For example for the x86 architecture the huge pages 
+size are 4KB, 2MB and 1GB pages. 
+% \subsection{Tailored page sizes}
+\subsection{TLB coalescing}
+This leverages the default OS allocator behavior to pack
+multiple PTEs into a single TLB entry.
 
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
+\subsection{Segment}
+A segment can be viewed as mapping between contiguous virtual
+memory and contiguous physical memory. The property of a 
+segment allows it to be larger than a page. Direct Segment
+<paper reference> allows the user to set a single segment
+for an application. Two registers are added to mark the start
+and end of the segment. Any virtual address within this region
+can be translated by adding the fixed offset between the virtual
+and physical address.
 
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
+\subsection{RMM}
+RMM introduces the concept of adding an additional range table.
+For large allocations RMM eagerly allocates contiguous physical pages.
+The following allocations creates large memory ranges that are
+both virtually and physically contiguous. RMM builds on the concept
+of Direct segment <paper reference> by adding offset to translate a virtual address 
+to physical address. RMM compares address with range boundaries 
+to decide which range it belongs to. RMM queries the range table 
+ofter an L1 TLB miss.
 
-\section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-anonymous initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
+\subsection{FlexPointer}
+FlexPointer is based on the RMM<paper reference RMM> paper. FlexPointer
+does eagerly allocate pages which are physically contiguous and stores the ID to translate a virtual address 
+to physical address on the remaining unused bits on the 64 bit virtual address. 
+The paper contribution mentions shifting the TLB lookup to an earlier stage to improve
+latency of accessing the TLB entries. FlexPointer immediate queries the 
+range TLB rather than the RMM paper which waits for the L1 TLB miss.
 
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
+% \section{Introduction}
+% ACM's consolidated article template, introduced in 2017, provides a
+% consistent \LaTeX\ style for use across ACM publications, and
+% incorporates accessibility and metadata-extraction functionality
+% necessary for future Digital Library endeavors. Numerous ACM and
+% SIG-specific \LaTeX\ templates have been examined, and their unique
+% features incorporated into this single new template.
 
-\subsection{Template Styles}
+% If you are new to publishing with ACM, this document is a valuable
+% guide to the process of preparing your work for publication. If you
+% have published with ACM before, this document provides insight and
+% instruction into more recent changes to the article template.
 
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
+% The ``\verb|acmart|'' document class can be used to prepare articles
+% for any ACM publication --- conference or journal, and for any stage
+% of publication, from review to final ``camera-ready'' copy, to the
+% author's own version, with {\itshape very} few changes to the source.
 
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\texttt{acmsmall}}: The default journal template style.
-\item {\texttt{acmlarge}}: Used by JOCCH and TAP.
-\item {\texttt{acmtog}}: Used by TOG.
-\end{itemize}
+% \section{Template Overview}
+% As noted in the introduction, the ``\verb|acmart|'' document class can
+% be used to prepare many different kinds of documentation --- a
+% double-anonymous initial submission of a full-length technical paper, a
+% two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
+% journal article, a SIGCHI Extended Abstract, and more --- all by
+% selecting the appropriate {\itshape template style} and {\itshape
+%   template parameters}.
 
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\texttt{sigconf}}: The default proceedings template style.
-\item{\texttt{sigchi}}: Used for SIGCHI conference articles.
-\item{\texttt{sigplan}}: Used for SIGPLAN conference articles.
-\end{itemize}
+% This document will explain the major features of the document
+% class. For further information, the {\itshape \LaTeX\ User's Guide} is
+% available from
+% \url{https://www.acm.org/publications/proceedings-template}.
 
-\subsection{Template Parameters}
+% \subsection{Template Styles}
 
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
+% The primary parameter given to the ``\verb|acmart|'' document class is
+% the {\itshape template style} which corresponds to the kind of publication
+% or SIG publishing the work. This parameter is enclosed in square
+% brackets and is a part of the {\verb|documentclass|} command:
+% \begin{verbatim}
+%   \documentclass[STYLE]{acmart}
+% \end{verbatim}
 
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\texttt{anonymous,review}}: Suitable for a ``double-anonymous''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \texttt{\acmSubmissionID} command to print the
-  submission's unique ID on each page of the work.
-\item{\texttt{authorversion}}: Produces a version of the work suitable
-  for posting by the author.
-\item{\texttt{screen}}: Produces colored hyperlinks.
-\end{itemize}
+% Journals use one of three template styles. All but three ACM journals
+% use the {\verb|acmsmall|} template style:
+% \begin{itemize}
+% \item {\texttt{acmsmall}}: The default journal template style.
+% \item {\texttt{acmlarge}}: Used by JOCCH and TAP.
+% \item {\texttt{acmtog}}: Used by TOG.
+% \end{itemize}
 
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[acmsmall,screen,review]{acmart}
-\end{verbatim}
+% The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
+% \begin{itemize}
+% \item {\texttt{sigconf}}: The default proceedings template style.
+% \item{\texttt{sigchi}}: Used for SIGCHI conference articles.
+% \item{\texttt{sigplan}}: Used for SIGPLAN conference articles.
+% \end{itemize}
 
-\section{Modifications}
+% \subsection{Template Parameters}
 
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
+% In addition to specifying the {\itshape template style} to be used in
+% formatting your work, there are a number of {\itshape template parameters}
+% which modify some part of the applied template style. A complete list
+% of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
 
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
+% Frequently-used parameters, or combinations of parameters, include:
+% \begin{itemize}
+% \item {\texttt{anonymous,review}}: Suitable for a ``double-anonymous''
+%   conference submission. Anonymizes the work and includes line
+%   numbers. Use with the \texttt{\acmSubmissionID} command to print the
+%   submission's unique ID on each page of the work.
+% \item{\texttt{authorversion}}: Produces a version of the work suitable
+%   for posting by the author.
+% \item{\texttt{screen}}: Produces colored hyperlinks.
+% \end{itemize}
 
-\section{Typefaces}
+% This document uses the following string as the first command in the
+% source file:
+% \begin{verbatim}
+% \documentclass[acmsmall,screen,review]{acmart}
+% \end{verbatim}
 
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
+% \section{Modifications}
 
-\section{Title Information}
+% Modifying the template --- including but not limited to: adjusting
+% margins, typeface sizes, line spacing, paragraph and list definitions,
+% and the use of the \verb|\vspace| command to manually adjust the
+% vertical spacing between elements of your work --- is not allowed.
 
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
+% {\bfseries Your document will be returned to you for revision if
+%   modifications are discovered.}
 
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
+% \section{Typefaces}
 
-\section{Authors and Affiliations}
+% The ``\verb|acmart|'' document class requires the use of the
+% ``Libertine'' typeface family. Your \TeX\ installation should include
+% this set of packages. Please do not substitute other typefaces. The
+% ``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
+% as they will override the built-in typeface families.
 
-Each author must be defined separately for accurate metadata
-identification.  As an exception, multiple authors may share one
-affiliation. Authors' names should not be abbreviated; use full first
-names wherever possible. Include authors' e-mail addresses whenever
-possible.
+% \section{Title Information}
 
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
+% The title of your work should use capital letters appropriately -
+% \url{https://capitalizemytitle.com/} has useful rules for
+% capitalization. Use the {\verb|title|} command to define the title of
+% your work. If your work has a subtitle, define it with the
+% {\verb|subtitle|} command.  Do not insert line breaks in your title.
 
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
+% If your title is lengthy, you must define a short version to be used
+% in the page headers, to prevent overlapping text. The \verb|title|
+% command has a ``short title'' parameter:
+% \begin{verbatim}
+%   \title[short title]{full title}
+% \end{verbatim}
 
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
+% \section{Authors and Affiliations}
 
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
+% Each author must be defined separately for accurate metadata
+% identification.  As an exception, multiple authors may share one
+% affiliation. Authors' names should not be abbreviated; use full first
+% names wherever possible. Include authors' e-mail addresses whenever
+% possible.
 
-Note that authors' addresses are mandatory for journal articles.
+% Grouping authors' names or e-mail addresses, or providing an ``e-mail
+% alias,'' as shown below, is not acceptable:
+% \begin{verbatim}
+%   \author{Brooke Aster, David Mehldau}
+%   \email{dave,judy,steve@university.edu}
+%   \email{firstname.lastname@phillips.org}
+% \end{verbatim}
 
-\section{Rights Information}
+% The \verb|authornote| and \verb|authornotemark| commands allow a note
+% to apply to multiple authors --- for example, if the first two authors
+% of an article contributed equally to the work.
 
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
+% If your author list is lengthy, you must define a shortened version of
+% the list of authors to be used in the page headers, to prevent
+% overlapping text. The following command should be placed just after
+% the last \verb|\author{}| definition:
+% \begin{verbatim}
+%   \renewcommand{\shortauthors}{McCartney, et al.}
+% \end{verbatim}
+% Omitting this command will force the use of a concatenated list of all
+% of the authors' names, which may result in overlapping text in the
+% page headers.
 
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
+% The article template's documentation, available at
+% \url{https://www.acm.org/publications/proceedings-template}, has a
+% complete explanation of these commands and tips for their effective
+% use.
 
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
+% Note that authors' addresses are mandatory for journal articles.
 
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
+% \section{Rights Information}
 
-\section{CCS Concepts and User-Defined Keywords}
+% Authors of any work published by ACM will need to complete a rights
+% form. Depending on the kind of work, and the rights management choice
+% made by the author, this may be copyright transfer, permission,
+% license, or an OA (open access) agreement.
 
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
+% Regardless of the rights management choice, the author will receive a
+% copy of the completed rights form once it has been submitted. This
+% form contains \LaTeX\ commands that must be copied into the source
+% document. When the document source is compiled, these commands and
+% their parameters add formatted text to several areas of the final
+% document:
+% \begin{itemize}
+% \item the ``ACM Reference Format'' text on the first page.
+% \item the ``rights management'' text on the first page.
+% \item the conference information in the page header(s).
+% \end{itemize}
 
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
+% Rights information is unique to the work; if you are preparing several
+% works for an event, make sure to use the correct set of commands with
+% each of the works.
 
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
+% The ACM Reference Format text is required for all articles over one
+% page in length, and is optional for one-page articles (abstracts).
 
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
+% \section{CCS Concepts and User-Defined Keywords}
 
-\section{Sectioning Commands}
+% Two elements of the ``acmart'' document class provide powerful
+% taxonomic tools for you to help readers find your work in an online
+% search.
 
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
+% The ACM Computing Classification System ---
+% \url{https://www.acm.org/publications/class-2012} --- is a set of
+% classifiers and concepts that describe the computing
+% discipline. Authors can select entries from this classification
+% system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
+% commands to be included in the \LaTeX\ source.
 
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
+% User-defined keywords are a comma-separated list of words and phrases
+% of the authors' choosing, providing a more flexible way of describing
+% the research being presented.
 
-\section{Tables}
+% CCS concepts and user-defined keywords are required for for all
+% articles over two pages in length, and are optional for one- and
+% two-page articles (or abstracts).
 
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
+% \section{Sectioning Commands}
 
-Table captions are placed {\itshape above} the table.
+% Your work should use standard \LaTeX\ sectioning commands:
+% \verb|section|, \verb|subsection|, \verb|subsubsection|, and
+% \verb|paragraph|. They should be numbered; do not remove the numbering
+% from the commands.
 
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
+% Simulating a sectioning command by setting the first word or words of
+% a paragraph in boldface or italicized text is {\bfseries not allowed.}
 
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
+% \section{Tables}
 
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
+% The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
+% package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
+% high-quality tables.
 
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
+% Table captions are placed {\itshape above} the table.
 
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
+% Because tables cannot be split across pages, the best placement for
+% them is typically the top of the page nearest their initial cite.  To
+% ensure this proper ``floating'' placement of tables, use the
+% environment \textbf{table} to enclose the table's contents and the
+% table caption.  The contents of the table itself must go in the
+% \textbf{tabular} environment, to be aligned properly in rows and
+% columns, with the desired horizontal and vertical rules.  Again,
+% detailed instructions on \textbf{tabular} material are found in the
+% \textit{\LaTeX\ User's Guide}.
 
-Always use midrule to separate table header rows from data rows, and
-use it only for this purpose. This enables assistive technologies to
-recognise table headers and support their users in navigating tables
-more easily.
+% Immediately following this sentence is the point at which
+% Table~\ref{tab:freq} is included in the input file; compare the
+% placement of the table here with the table in the printed output of
+% this document.
 
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
+% \begin{table}
+%   \caption{Frequency of Special Characters}
+%   \label{tab:freq}
+%   \begin{tabular}{ccl}
+%     \toprule
+%     Non-English or Math&Frequency&Comments\\
+%     \midrule
+%     \O & 1 in 1,000& For Swedish names\\
+%     $\pi$ & 1 in 5& Common in math\\
+%     \$ & 4 in 5 & Used in business\\
+%     $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
+%   \bottomrule
+% \end{tabular}
+% \end{table}
 
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
+% To set a wider table, which takes up the whole width of the page's
+% live area, use the environment \textbf{table*} to enclose the table's
+% contents and the table caption.  As with a single-column table, this
+% wide table will ``float'' to a location deemed more
+% desirable. Immediately following this sentence is the point at which
+% Table~\ref{tab:commands} is included in the input file; again, it is
+% instructive to compare the placement of the table here with the table
+% in the printed output of this document.
 
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
+% \begin{table*}
+%   \caption{Some Typical Commands}
+%   \label{tab:commands}
+%   \begin{tabular}{ccl}
+%     \toprule
+%     Command &A Number & Comments\\
+%     \midrule
+%     \texttt{{\char'134}author} & 100& Author \\
+%     \texttt{{\char'134}table}& 300 & For tables\\
+%     \texttt{{\char'134}table*}& 400& For wider tables\\
+%     \bottomrule
+%   \end{tabular}
+% \end{table*}
 
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
+% Always use midrule to separate table header rows from data rows, and
+% use it only for this purpose. This enables assistive technologies to
+% recognise table headers and support their users in navigating tables
+% more easily.
 
-\section{Figures}
+% \section{Math Equations}
+% You may want to display math equations in three distinct styles:
+% inline, numbered or non-numbered display.  Each of the three are
+% discussed in the next sections.
 
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
+% \subsection{Inline (In-text) Equations}
+% A formula that appears in the running text is called an inline or
+% in-text formula.  It is produced by the \textbf{math} environment,
+% which can be invoked with the usual
+% \texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
+% the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
+% and structures, from $\alpha$ to $\omega$, available in
+% \LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
+% examples of in-text equations in context. Notice how this equation:
+% \begin{math}
+%   \lim_{n\rightarrow \infty}x=0
+% \end{math},
+% set here in in-line math style, looks slightly different when
+% set in display style.  (See next section).
+
+% \subsection{Display Equations}
+% A numbered display equation---one set off by vertical space from the
+% text and centered horizontally---is produced by the \textbf{equation}
+% environment. An unnumbered display equation is produced by the
+% \textbf{displaymath} environment.
+
+% Again, in either environment, you can use any of the symbols and
+% structures available in \LaTeX\@; this section will just give a couple
+% of examples of display equations in context.  First, consider the
+% equation, shown as an inline equation above:
+% \begin{equation}
+%   \lim_{n\rightarrow \infty}x=0
+% \end{equation}
+% Notice how it is formatted somewhat differently in
+% the \textbf{displaymath}
+% environment.  Now, we'll enter an unnumbered equation:
+% \begin{displaymath}
+%   \sum_{i=0}^{\infty} x + 1
+% \end{displaymath}
+% and follow it with another numbered equation:
+% \begin{equation}
+%   \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
+% \end{equation}
+% just to demonstrate \LaTeX's able handling of numbering.
+
+% \section{Figures}
+
+% The ``\verb|figure|'' environment should be used for figures. One or
+% more images can be placed within a figure. If your figure contains
+% third-party material, you must clearly identify it as such, as shown
+% in the example below.
 % \begin{figure}[h]
@@
 
-Your figures should contain a caption which describes the figure to
-the reader.
+% Your figures should contain a caption which describes the figure to
+% the reader.
 
-Figure captions are placed {\itshape below} the figure.
+% Figure captions are placed {\itshape below} the figure.
 
-Every figure should also have a figure description unless it is purely
-decorative. These descriptions convey what’s in the image to someone
-who cannot see it. They are also used by search engine crawlers for
-indexing images, and when images cannot be loaded.
+% Every figure should also have a figure description unless it is purely
+% decorative. These descriptions convey what’s in the image to someone
+% who cannot see it. They are also used by search engine crawlers for
+% indexing images, and when images cannot be loaded.
 
-A figure description must be unformatted plain text less than 2000
-characters long (including spaces).  {\bfseries Figure descriptions
-  should not repeat the figure caption – their purpose is to capture
-  important information that is not already provided in the caption or
-  the main text of the paper.} For figures that convey important and
-complex new information, a short text description may not be
-adequate. More complex alternative descriptions can be placed in an
-appendix and referenced in a short figure description. For example,
-provide a data table capturing the information in a bar chart, or a
-structured list representing a graph.  For additional information
-regarding how best to write figure descriptions and why doing this is
-so important, please see
-\url{https://www.acm.org/publications/taps/describing-figures/}.
+% A figure description must be unformatted plain text less than 2000
+% characters long (including spaces).  {\bfseries Figure descriptions
+%   should not repeat the figure caption – their purpose is to capture
+%   important information that is not already provided in the caption or
+%   the main text of the paper.} For figures that convey important and
+% complex new information, a short text description may not be
+% adequate. More complex alternative descriptions can be placed in an
+% appendix and referenced in a short figure description. For example,
+% provide a data table capturing the information in a bar chart, or a
+% structured list representing a graph.  For additional information
+% regarding how best to write figure descriptions and why doing this is
+% so important, please see
+% \url{https://www.acm.org/publications/taps/describing-figures/}.
 
-\subsection{The ``Teaser Figure''}
+% \subsection{The ``Teaser Figure''}
 
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
+% A ``teaser figure'' is an image, or set of images in one figure, that
+% are placed after all author and affiliation information, and before
+% the body of the article, spanning the page. If you wish to have such a
+% figure in your article, place the command immediately before the
+% \verb|\maketitle| command:
+% \begin{verbatim}
+%   \begin{teaserfigure}
+%     \includegraphics[width=\textwidth]{sampleteaser}
+%     \caption{figure caption}
+%     \Description{figure description}
+%   \end{teaserfigure}
+% \end{verbatim}
 
-\section{Citations and Bibliographies}
+% \section{Citations and Bibliographies}
 
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
+% The use of \BibTeX\ for the preparation and formatting of one's
+% references is strongly recommended. Authors' names should be complete
+% --- use full first names (``Donald E. Knuth'') not initials
+% (``D. E. Knuth'') --- and the salient identifying features of a
+% reference should be included: title, year, volume, number, pages,
+% article DOI, etc.
 
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
+% The bibliography is included in your source document with these two
+% commands, placed just before the \verb|\end{document}| command:
+% \begin{verbatim}
+%   \bibliographystyle{ACM-Reference-Format}
+%   \bibliography{bibfile}
+% \end{verbatim}
+% where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
+% suffix, of the \BibTeX\ file.
 
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before the command
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
+% Citations and references are numbered by default. A small number of
+% ACM publications have citations and references formatted in the
+% ``author year'' style; for these exceptions, please include this
+% command in the {\bfseries preamble} (before the command
+% ``\verb|\begin{document}|'') of your \LaTeX\ source:
+% \begin{verbatim}
+%   \citestyle{acmauthoryear}
+% \end{verbatim}
 
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, a couple of articles in a proceedings (of a
-  conference, symposium, workshop for example) (paginated proceedings
-  article) \cite{Andler79, Hagerup1993}, a proceedings article with
-  all possible elements \cite{Smith10}, an example of an enumerated
-  proceedings article \cite{VanGundy07}, an informally published work
-  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
-    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
-  master's thesis: \cite{anisi03}, an online document / world wide web
-  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
-  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
-  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
-  Artifacts: \cite{R} and \cite{UMassCitations}.
+  % Some examples.  A paginated journal article \cite{Abril07}, an
+  % enumerated journal article \cite{Cohen07}, a reference to an entire
+  % issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
+  % monograph/whole book in a series (see 2a in spec. document)
+  % \cite{Harel79}, a divisible-book such as an anthology or compilation
+  % \cite{Editor00} followed by the same example, however we only output
+  % the series if the volume number is given \cite{Editor00a} (so
+  % Editor00a's series should NOT be present since it has no vol. no.),
+  % a chapter in a divisible book \cite{Spector90}, a chapter in a
+  % divisible book in a series \cite{Douglass98}, a multi-volume work as
+  % book \cite{Knuth97}, a couple of articles in a proceedings (of a
+  % conference, symposium, workshop for example) (paginated proceedings
+  % article) \cite{Andler79, Hagerup1993}, a proceedings article with
+  % all possible elements \cite{Smith10}, an example of an enumerated
+  % proceedings article \cite{VanGundy07}, an informally published work
+  % \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
+  %   AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
+  % master's thesis: \cite{anisi03}, an online document / world wide web
+  % resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
+  % (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
+  % and (Case 3) a patent \cite{JoeScientist001}, work accepted for
+  % publication \cite{rous08}, 'YYYYb'-test for prolific author
+  % \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
+  % contain 'duplicate' DOI and URLs (some SIAM articles)
+  % \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
+  % multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
+  % couple of citations with DOIs:
+  % \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
+  % citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
+  % Artifacts: \cite{R} and \cite{UMassCitations}.
 
-\section{Acknowledgments}
+% \section{Acknowledgments}
 
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
+% Identification of funding sources and other support, and thanks to
+% individuals and groups that assisted in the research and the
+% preparation of the work should be included in an acknowledgment
+% section, which is placed just before the reference section in your
+% document.
 
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
+% This section has a special environment:
+% \begin{verbatim}
+%   \begin{acks}
+%   ...
+%   \end{acks}
+% \end{verbatim}
+% so that the information contained therein can be more easily collected
+% during the article metadata extraction phase, and to ensure
+% consistency in the spelling of the section heading.
 
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
+% Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
 
-\section{Appendices}
+% \section{Appendices}
 
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
+% If your work needs an appendix, add it before the
+% ``\verb|\end{document}|'' command at the conclusion of your source
+% document.
 
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
+% Start the appendix with the ``\verb|appendix|'' command:
+% \begin{verbatim}
+%   \appendix
+% \end{verbatim}
+% and note that in the appendix, sections are lettered, not
+% numbered. This document has two appendices, demonstrating the section
+% and subsection identification method.
 
-\section{Multi-language papers}
+% \section{Multi-language papers}
 
-Papers may be written in languages other than English or include
-titles, subtitles, keywords and abstracts in different languages (as a
-rule, a paper in a language other than English should include an
-English title and an English abstract).  Use \verb|language=...| for
-every language used in the paper.  The last language indicated is the
-main language of the paper.  For example, a French paper with
-additional titles and abstracts in English and German may start with
-the following command
-\begin{verbatim}
-\documentclass[sigconf, language=english, language=german,
-               language=french]{acmart}
-\end{verbatim}
+% Papers may be written in languages other than English or include
+% titles, subtitles, keywords and abstracts in different languages (as a
+% rule, a paper in a language other than English should include an
+% English title and an English abstract).  Use \verb|language=...| for
+% every language used in the paper.  The last language indicated is the
+% main language of the paper.  For example, a French paper with
+% additional titles and abstracts in English and German may start with
+% the following command
+% \begin{verbatim}
+% \documentclass[sigconf, language=english, language=german,
+%                language=french]{acmart}
+% \end{verbatim}
 
-The title, subtitle, keywords and abstract will be typeset in the main
-language of the paper.  The commands \verb|\translatedXXX|, \verb|XXX|
-begin title, subtitle and keywords, can be used to set these elements
-in the other languages.  The environment \verb|translatedabstract| is
-used to set the translation of the abstract.  These commands and
-environment have a mandatory first argument: the language of the
-second argument.  See \verb|sample-sigconf-i13n.tex| file for examples
-of their usage.
+% The title, subtitle, keywords and abstract will be typeset in the main
+% language of the paper.  The commands \verb|\translatedXXX|, \verb|XXX|
+% begin title, subtitle and keywords, can be used to set these elements
+% in the other languages.  The environment \verb|translatedabstract| is
+% used to set the translation of the abstract.  These commands and
+% environment have a mandatory first argument: the language of the
+% second argument.  See \verb|sample-sigconf-i13n.tex| file for examples
+% of their usage.
 
-\section{SIGCHI Extended Abstracts}
+% \section{SIGCHI Extended Abstracts}
 
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{description}
-\item[\texttt{sidebar}:]  Place formatted text in the margin.
-\item[\texttt{marginfigure}:] Place a figure in the margin.
-\item[\texttt{margintable}:] Place a table in the margin.
-\end{description}
+% The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
+% not in Word) produces a landscape-orientation formatted article, with
+% a wide left margin. Three environments are available for use with the
+% ``\verb|sigchi-a|'' template style, and produce formatted output in
+% the margin:
+% \begin{description}
+% \item[\texttt{sidebar}:]  Place formatted text in the margin.
+% \item[\texttt{marginfigure}:] Place a figure in the margin.
+% \item[\texttt{margintable}:] Place a table in the margin.
+% \end{description}
 
@@
 
-\section{Research Methods}
+% \section{Research Methods}
 
-\subsection{Part One}
+% \subsection{Part One}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
+% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
+% malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
+% sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
+% vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
+% lacinia dolor. Integer ultricies commodo sem nec semper.
 
-\subsection{Part Two}
+% \subsection{Part Two}
 
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
+% Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
+% ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
+% ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
+% eros. Vivamus non purus placerat, scelerisque diam eu, cursus
+% ante. Etiam aliquam tortor auctor efficitur mattis.
 
-\section{Online Resources}
+% \section{Online Resources}
 
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
+% Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
+% pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
+% enim maximus. Vestibulum gravida massa ut felis suscipit
+% congue. Quisque mattis elit a risus ultrices commodo venenatis eget
+% dui. Etiam sagittis eleifend elementum.
 
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
+% Nam interdum magna at lectus dignissim, ac dignissim lorem
+% rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
+% massa et mattis lacinia.
 

### 2024-02-25 papers/ISMM/FlexPointer/paper.tex
commented out TLB coalesing

@@
 % \subsection{Tailored page sizes}
-\subsection{TLB coalescing}
-This leverages the default OS allocator behavior to pack
-multiple PTEs into a single TLB entry.
+% TODO later
+% \subsection{TLB coalescing}
+% This leverages the default OS allocator behavior to pack
+% multiple PTEs into a single TLB entry.
 
@@
 latency of accessing the TLB entries. FlexPointer immediate queries the 
-range TLB rather than the RMM paper which waits for the L1 TLB miss.
+range TLB for translations rather than the RMM paper which waits for the L1 TLB miss.
 

### 2024-02-25 papers/ISMM/FlexPointer/paper.tex
added base structure

@@
 \begin{abstract}
-  The gap between application workloads and capacity of TLB is on the 
-  rise. Previous work exploits this by physically contiguous 
-  memory. Capability-based addressing in the CHERI architecture is 
-  designed to improve hardware-level system security.
-  These security mechanisms designed in place can also 
-  behave as accelerators to standard user-space memory allocators. 
-  The property of CHERI which is to use FAT-Pointers to store
-  the upper and lower bounds can also be represented as ranges of 
-  memory addresses which are physically contiguous. 
-  <Talking about the results>.
+  % Draft 1
+  % The gap between application workloads and capacity of TLB is on the 
+  % rise. Previous work exploits this by physically contiguous 
+  % memory. Capability-based addressing in the CHERI architecture is 
+  % designed to improve hardware-level system security.
+  % These security mechanisms designed in place can also 
+  % behave as accelerators to standard user-space memory allocators. 
+  % The property of CHERI which is to use FAT-Pointers to store
+  % the upper and lower bounds can also be represented as ranges of 
+  % memory addresses which are physically contiguous. 
+  % <Talking about the results>.
+  % Draft 2
+  The increasing disparity between application workloads and the capacity of Translation Lookaside Buffers (TLB) 
+  has prompted researchers to explore innovative solutions to mitigate this gap. One such approach involves 
+  leveraging physically contiguous memory to optimize TLB utilization. Concurrently, advancements in hardware-level 
+  system security, exemplified by the Capability Hardware Enhanced RISC Instructions (CHERI) architecture, offer 
+  additional opportunities for improving memory management and security.
+
+ CHERI introduces capability-based addressing, a novel approach that enhances system security by associating capabilities 
+ with memory pointers. These capabilities restrict access to memory regions, thereby fortifying the system against various 
+ security threats. Importantly, the mechanisms implemented in CHERI for enforcing memory protection can also serve as 
+ accelerators for standard user-space memory allocators. By leveraging capability-based addressing, memory 
+ allocators can efficiently manage memory resources while ensuring robust security measures are in place.
 \end{abstract}
@@
 
-\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+% \ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+% \ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+% \ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+% \ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
-  Your, Paper}
+% \keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
+%   Your, Paper}
 
-\received{20 February 2007}
-\received[revised]{12 March 2009}
-\received[accepted]{5 June 2009}
+% \received{20 February 2007}
+% \received[revised]{12 March 2009}
+% \received[accepted]{5 June 2009}
 
@@
 
+\section{Introduction}
+
+\section{FAT-Pointer based range addresses}
+
+\subsection{Overview}
+
+\subsection{Range creation}
+
+\subsection{Allocation with huge pages}
+
+\section{Evaluation}
+
+\section{Limitations}
+
 \section{Related work}
+Efficient memory management, particularly in the context of 
+Translation Lookaside Buffer (TLB) optimization, has been a focal point of 
+research and development within computer architecture. Various techniques have been 
+proposed to mitigate TLB-related bottlenecks and improve overall system performance.
+
 \subsection{Huge Pages}
@@
 range TLB for translations rather than the RMM paper which waits for the L1 TLB miss.
+
+\section{Summary}
 

### 2024-02-29 example/TestBenchmarks/simpleMemoryAllocAndFree/test.c
address really simple malloc and free command to debug slow run times

@@ -1,0 +1,14 @@
+#include <assert.h>
+#include <stdio.h>
+#include <stdlib.h>
+
+int main(int argc, char **argv)
+{
+  size_t size = 10000000345345;
+  void *mem = malloc(size);
+  printf("Successfully malloc'd %zu bytes at addr %p\n", size, mem);
+  assert(mem != NULL);
+  free(mem);
+  printf("Successfully free'd %zu bytes from addr %p\n", size, mem);
+  return 0;
+}

### 2024-02-29 example/TestBenchmarks/simpleMemoryAllocAndFree/run.sh
added latest run.sh from morello

@@ -1,0 +1,2 @@
+cc -g -Wall -o -mabi=purecap-benchmarkest test.c
+

### 2024-02-29 example/TestBenchmarks/simpleMemoryAllocAndFree/test.c

@@ -4,7 +4,7 @@
 
 int main(int argc, char **argv)
 {
-  size_t size = 10000000345345;
+  size_t size = 1000000000;
   void *mem = malloc(size);
   printf("Successfully malloc'd %zu bytes at addr %p\n", size, mem);
   assert(mem != NULL);

### 2024-03-01 example/TestBenchmarks/simpleMemoryAllocAndFree/ContigTest/test.c
added contig smaller tests

@@ -1,0 +1,87 @@
+#include <assert.h>
+#include <stdio.h>
+#include <stdlib.h>
+
+#ifndef __USE_GNU
+#  define __USE_GNU
+#endif
+
+#ifndef _GNU_SOURCE
+#  define _GNU_SOURCE
+#endif
+
+#include <dlfcn.h>
+#include <stdint.h>
+#include <string.h> /* for memcpy hack below */
+#include <sys/fcntl.h>
+#include <sys/mman.h>
+
+#define FILENAME "/dev/contigmem"
+
+int main(int argc, char **argv)
+{ 
+  // 1 GB 
+  // size_t size = 1000000000;
+  
+  // smaller size
+  size_t size = 1000;
+  void *mem = malloc(size);
+  printf("Successfully malloc'd %zu bytes at addr %p\n", size, mem);
+  assert(mem != NULL);
+  free(mem);
+  printf("Successfully free'd %zu bytes from addr %p\n", size, mem);
+  return 0;
+}
+
+static inline void *MALLOC(size_t size)
+{
+//    void * temp = malloc(size);
+//    assert(temp);
+//    return temp;
+
+// Ensuring malloc this is mmap and phyiscally contigous
+    int fd = open
+	(FILENAME, O_RDWR | O_CREAT, 0600);
+	if (fd < 0) {
+		perror("open");
+		exit(EXIT_FAILURE);
+	}
+
+	off_t offset = 0; // offset to seek to.
+
+	if (ftruncate(fd, size) < 0) {
+		perror("ftruncate");
+		close(fd);
+		exit(EXIT_FAILURE);
+	}
+
+	int *ptr = mmap(NULL, size,
+	                         PROT_READ | PROT_WRITE, MAP_SHARED,
+	                         fd, offset);
+	if(ptr == MAP_FAILED)
+	{
+		perror("mmap");
+		exit(EXIT_FAILURE);
+	}
+
+    *ptr = size;
+
+    return ptr;
+   // void *ptr = malloc(size);
+   // return ptr;
+}
+
+
+static inline void *FREE(void *ptr)
+{
+    int *pt = ptr;
+    size_t size;
+    --pt;
+    size = *pt;
+    if(munmap(pt, size) == -1)
+	{
+		perror("munmap");
+		exit(EXIT_FAILURE);
+	}
+   // free(ptr);
+}

### 2024-03-01 example/TestBenchmarks/simpleMemoryAllocAndFree/ContigTest/test.c
small bug fix

@@ -25,10 +25,10 @@ int main(int argc, char **argv)
   
   // smaller size
   size_t size = 1000;
-  void *mem = malloc(size);
+  void *mem = MALLOC(size);
   printf("Successfully malloc'd %zu bytes at addr %p\n", size, mem);
   assert(mem != NULL);
-  free(mem);
+  FREE(mem);
   printf("Successfully free'd %zu bytes from addr %p\n", size, mem);
   return 0;
 }

### 2024-03-01 example/TestBenchmarks/simpleMemoryAllocAndFree/ContigTest/test.c
removed static declaration

@@ -33,7 +33,7 @@ int main(int argc, char **argv)
   return 0;
 }
 
-static inline void *MALLOC(size_t size)
+void *MALLOC(size_t size)
 {
 //    void * temp = malloc(size);
 //    assert(temp);
@@ -72,7 +72,7 @@ static inline void *MALLOC(size_t size)
 }
 
 
-static inline void *FREE(void *ptr)
+void *FREE(void *ptr)
 {
     int *pt = ptr;
     size_t size;

### 2024-03-01 example/TestBenchmarks/simpleMemoryAllocAndFree/ContigTest/test.c
removed static declaration

@@ -25,15 +25,54 @@ int main(int argc, char **argv)
   
   // smaller size
   size_t size = 1000;
-  void *mem = MALLOC(size);
+
+  // Custom malloc
+  int fd = open
+	(FILENAME, O_RDWR | O_CREAT, 0600);
+	if (fd < 0) {
+		perror("open");
+		exit(EXIT_FAILURE);
+	}
+
+	off_t offset = 0; // offset to seek to.
+
+	if (ftruncate(fd, size) < 0) {
+		perror("ftruncate");
+		close(fd);
+		exit(EXIT_FAILURE);
+	}
+
+	int *ptr = mmap(NULL, size,
+	                         PROT_READ | PROT_WRITE, MAP_SHARED,
+	                         fd, offset);
+	if(ptr == MAP_FAILED)
+	{
+		perror("mmap");
+		exit(EXIT_FAILURE);
+	}
+
+    *ptr = size;
+
+
   printf("Successfully malloc'd %zu bytes at addr %p\n", size, mem);
   assert(mem != NULL);
-  FREE(mem);
+
+  // Custom free 
+  int *pt = ptr;
+    size_t size;
+    --pt;
+    size = *pt;
+    if(munmap(pt, size) == -1)
+	{
+		perror("munmap");
+		exit(EXIT_FAILURE);
+  }
+  
   printf("Successfully free'd %zu bytes from addr %p\n", size, mem);
   return 0;
 }
 
-void *MALLOC(size_t size)
+static inline void *MALLOC(size_t size)
 {
 //    void * temp = malloc(size);
 //    assert(temp);
@@ -72,7 +111,7 @@ void *MALLOC(size_t size)
 }
 
 
-void *FREE(void *ptr)
+static inline void *FREE(void *ptr)
 {
     int *pt = ptr;
     size_t size;

### 2024-03-01 example/TestBenchmarks/simpleMemoryAllocAndFree/ContigTest/test.c
fixed undelclared memory

@@ -54,8 +54,8 @@ int main(int argc, char **argv)
     *ptr = size;
 
 
-  printf("Successfully malloc'd %zu bytes at addr %p\n", size, mem);
-  assert(mem != NULL);
+  printf("Successfully malloc'd %zu bytes at addr %p\n", size, ptr);
+  assert(ptr != NULL);
 
   // Custom free 
   int *pt = ptr;
@@ -67,8 +67,8 @@ int main(int argc, char **argv)
 		perror("munmap");
 		exit(EXIT_FAILURE);
   }
-  
-  printf("Successfully free'd %zu bytes from addr %p\n", size, mem);
+
+  printf("Successfully free'd %zu bytes from addr %p\n", size, ptr);
   return 0;
 }
 

### 2024-03-01 example/TestBenchmarks/simpleMemoryAllocAndFree/ContigTest/test.c
fixed redefinition of size

@@ -59,7 +59,7 @@ int main(int argc, char **argv)
 
   // Custom free 
   int *pt = ptr;
-    size_t size;
+    // size_t size;
     --pt;
     size = *pt;
     if(munmap(pt, size) == -1)

### 2024-03-01 example/TestBenchmarks/simpleMemoryAllocAndFree/ContigTest/test.c
checking if problem with Free

@@ -58,15 +58,15 @@ int main(int argc, char **argv)
   assert(ptr != NULL);
 
   // Custom free 
-  int *pt = ptr;
-    // size_t size;
-    --pt;
-    size = *pt;
-    if(munmap(pt, size) == -1)
-	{
-		perror("munmap");
-		exit(EXIT_FAILURE);
-  }
+  // int *pt = ptr;
+  //   // size_t size;
+  //   --pt;
+  //   size = *pt;
+  //   if(munmap(pt, size) == -1)
+	// {
+	// 	perror("munmap");
+	// 	exit(EXIT_FAILURE);
+  // }
 
   printf("Successfully free'd %zu bytes from addr %p\n", size, ptr);
   return 0;

### 2024-03-01 example/TestBenchmarks/simpleMemoryAllocAndFree/ContigTest/test.c
test larger size

@@ -21,10 +21,10 @@
 int main(int argc, char **argv)
 { 
   // 1 GB 
-  // size_t size = 1000000000;
+  size_t size = 1000000000;
   
   // smaller size
-  size_t size = 1000;
+  //size_t size = 1000;
 
   // Custom malloc
   int fd = open

### 2024-03-01 example/TestBenchmarks/simpleMemoryAllocAndFree/ContigTest/test.c
added to check memory file size of contig memory

@@ -15,6 +15,7 @@
 #include <string.h> /* for memcpy hack below */
 #include <sys/fcntl.h>
 #include <sys/mman.h>
+#include <sys/stat.h>
 
 #define FILENAME "/dev/contigmem"
 
@@ -33,94 +34,98 @@ int main(int argc, char **argv)
 		perror("open");
 		exit(EXIT_FAILURE);
 	}
+  struct stat st;
+  stat(FILENAME, &st);
+  size = st.st_size;
+  printf(size);
 
-	off_t offset = 0; // offset to seek to.
+// 	off_t offset = 0; // offset to seek to.
 
-	if (ftruncate(fd, size) < 0) {
-		perror("ftruncate");
-		close(fd);
-		exit(EXIT_FAILURE);
-	}
+// 	if (ftruncate(fd, size) < 0) {
+// 		perror("ftruncate");
+// 		close(fd);
+// 		exit(EXIT_FAILURE);
+// 	}
 
-	int *ptr = mmap(NULL, size,
-	                         PROT_READ | PROT_WRITE, MAP_SHARED,
-	                         fd, offset);
-	if(ptr == MAP_FAILED)
-	{
-		perror("mmap");
-		exit(EXIT_FAILURE);
-	}
+// 	int *ptr = mmap(NULL, size,
+// 	                         PROT_READ | PROT_WRITE, MAP_SHARED,
+// 	                         fd, offset);
+// 	if(ptr == MAP_FAILED)
+// 	{
+// 		perror("mmap");
+// 		exit(EXIT_FAILURE);
+// 	}
 
-    *ptr = size;
-
-
-  printf("Successfully malloc'd %zu bytes at addr %p\n", size, ptr);
-  assert(ptr != NULL);
-
-  // Custom free 
-  // int *pt = ptr;
-  //   // size_t size;
-  //   --pt;
-  //   size = *pt;
-  //   if(munmap(pt, size) == -1)
-	// {
-	// 	perror("munmap");
-	// 	exit(EXIT_FAILURE);
-  // }
-
-  printf("Successfully free'd %zu bytes from addr %p\n", size, ptr);
-  return 0;
-}
-
-static inline void *MALLOC(size_t size)
-{
-//    void * temp = malloc(size);
-//    assert(temp);
-//    return temp;
-
-// Ensuring malloc this is mmap and phyiscally contigous
-    int fd = open
[…]

### 2024-03-01 example/TestBenchmarks/simpleMemoryAllocAndFree/ContigTest/test.c
trying smaller space again

@@ -22,10 +22,10 @@
 int main(int argc, char **argv)
 { 
   // 1 GB 
-  size_t size = 1000000000;
+  // size_t size = 1000000000;
   
   // smaller size
-  //size_t size = 1000;
+  size_t size = 1000000;
 
   // Custom malloc
   int fd = open
@@ -34,98 +34,102 @@ int main(int argc, char **argv)
 		perror("open");
 		exit(EXIT_FAILURE);
 	}
-  struct stat st;
-  stat(FILENAME, &st);
-  size = st.st_size;
-  printf(size);
 
-// 	off_t offset = 0; // offset to seek to.
-
-// 	if (ftruncate(fd, size) < 0) {
-// 		perror("ftruncate");
-// 		close(fd);
-// 		exit(EXIT_FAILURE);
-// 	}
-
-// 	int *ptr = mmap(NULL, size,
-// 	                         PROT_READ | PROT_WRITE, MAP_SHARED,
-// 	                         fd, offset);
-// 	if(ptr == MAP_FAILED)
-// 	{
-// 		perror("mmap");
-// 		exit(EXIT_FAILURE);
-// 	}
-
-//     *ptr = size;
+  // Cannot read in security exception 
+  // on reads
+  // struct stat st;
+  // stat(FILENAME, &st);
+  // size = st.st_size;
+  // printf(size);
 
 
-//   printf("Successfully malloc'd %zu bytes at addr %p\n", size, ptr);
-//   assert(ptr != NULL);
+	off_t offset = 0; // offset to seek to.
 
-//   // Custom free 
-//   // int *pt = ptr;
-//   //   // size_t size;
-//   //   --pt;
-//   //   size = *pt;
-//   //   if(munmap(pt, size) == -1)
-// 	// {
-// 	// 	perror("munmap");
-// 	// 	exit(EXIT_FAILURE);
-//   // }
+	if (ftruncate(fd, size) < 0) {
+		perror("ftruncate");
+		close(fd);
+		exit(EXIT_FAILURE);
+	}
 
-//   printf("Successfully free'd %zu bytes from addr %p\n", size, ptr);
-//   return 0;
-// }
+	int *ptr = mmap(NULL, size,
+	                         PROT_READ | PROT_WRITE, MAP_SHARED,
+	                         fd, offset);
+	if(ptr == MAP_FAILED)
+	{
+		perror("mmap");
[…]

### 2024-03-10 papers/ISMM/FlexPointer/paper.tex
added .gitignore entry for binaries
references set

@@
 \documentclass[acmsmall,screen,review]{acmart}
+
+% \usepackage[style=authoryear, useprefix = false]{biblatex}
 
@@
 
+\subsection{Background}
+
 \section{FAT-Pointer based range addresses}
+This experiment exploits the FAT pointer to enable faster
 
@@
 \subsection{Range creation}
+
+\subsection{Fragmentation}
 
@@
 Efficient memory management, particularly in the context of 
-Translation Lookaside Buffer (TLB) optimization, has been a focal point of 
+Translation Lookaside Buffer (TLB) optimization \cite{ad-wood-2003}, has been a focal point of 
 research and development within computer architecture. Various techniques have been 
@@
 %% consistent spelling of the heading.
+% \begin{acks}
+% To Robert, for the bagels and explaining CMYK and color spaces.
+% \end{acks}
+
 \begin{acks}
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
+\bibliography{references}
 
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
+% \appendix
 

### 2024-03-11 papers/ISMM/FlexPointer/paper.tex
added introduction section

@@
 
+% Sample citation
+% \cite{ad-wood-2003}
+
 %%
@@
 \section{Introduction}
+In the dynamic landscape of computing, the pursuit of optimal performance is a constant endeavor, 
+especially as applications evolve to handle increasingly complex workloads. 
+One critical aspect influencing performance is memory management, where efficient 
+utilization of resources is paramount. Translation Lookaside Buffers (TLBs) play a 
+pivotal role in this regard, expediting memory access by storing recently accessed memory translations.
+However, as applications grow in size and complexity, the capacity of TLBs often struggles to 
+keep pace, leading to performance bottlenecks. To address this challenge, researchers have 
+turned to innovative solutions, one of which involves harnessing the benefits of huge pages.
+Huge pages, also known as large pages, allow for the allocation of memory in significantly 
+larger chunks compared to traditional small pages. By reducing the number of TLB entries 
+needed to access a given amount of memory, huge pages offer a potential avenue for optimizing 
+TLB utilization and thereby enhancing overall system performance.
 
+Simultaneously, advancements in hardware-level security, such as the Capability Hardware 
+Enhanced RISC Instructions (CHERI) architecture, present additional opportunities for 
+performance enhancement. CHERI's capability-based addressing approach not only strengthens 
+system security by tightly controlling memory access but also provides avenues for 
+accelerating memory management operations.
+
+In this context, the integration of huge pages into memory management 
+strategies alongside capability-based addressing in architectures like 
+CHERI offers a compelling synergy. By optimizing TLB utilization through the 
+utilization of huge pages and leveraging the security features of capability-based addressing, 
+significant performance improvements can be realized. This approach not only enhances 
+system security but also accelerates memory access
+
+% TODO: 
+% - Add references for FlexPointer, Range Memory Mapping (RMM), Direct Segment and Huge Pages
 \subsection{Background}
+Efficient memory management, particularly in the context of 
+Translation Lookaside Buffer (TLB) optimization, has been a focal point of 
+research and development within computer architecture. Various techniques have been 
+proposed to mitigate TLB-related bottlenecks and improve overall system performance.
+
+\subsubsection{Huge Pages:}
+This is used to map a very large region of memory to a 
+single entry. This small/large region of memory is physically
+contiguous. Most implementations of huge pages are size
+aligned, For example for the x86 architecture the huge pages 
+size are 4KB, 2MB and 1GB pages. 
+% \subsection{Tailored page sizes}
+% TODO later
+% \subsection{TLB coalescing}
+% This leverages the default OS allocator behavior to pack
+% multiple PTEs into a single TLB entry.
+
+\subsubsection{Segment:}
+A segment can be viewed as mapping between contiguous virtual
+memory and contiguous physical memory. The property of a 
+segment allows it to be larger than a page. Direct Segment
+<paper reference> allows the user to set a single segment
+for an application. Two registers are added to mark the start
+and end of the segment. Any virtual address within this region
+can be translated by adding the fixed offset between the virtual
+and physical address.
+
+\subsubsection{RMM:}
+RMM introduces the concept of adding an additional range table.
+For large allocations RMM eagerly allocates contiguous physical pages.
+The following allocations creates large memory ranges that are
+both virtually and physically contiguous. RMM builds on the concept
+of Direct segment <paper reference> by adding offset to translate a virtual address 
+to physical address. RMM compares address with range boundaries 
+to decide which range it belongs to. RMM queries the range table 
+ofter an L1 TLB miss.
+
+\subsubsection{FlexPointer:}
+FlexPointer is based on the RMM<paper reference RMM> paper. FlexPointer
+does eagerly allocate pages which are physically contiguous and stores the ID to translate a virtual address 
+to physical address on the remaining unused bits on the 64 bit virtual address. 
+The paper contribution mentions shifting the TLB lookup to an earlier stage to improve
+latency of accessing the TLB entries. FlexPointer immediate queries the 
+range TLB for translations rather than the RMM paper which waits for the L1 TLB miss.
 
@@
 
+% TODO: 
+% - Add references for FlexPointer, Range Memory Mapping (RMM) and Direct segment
 \subsection{Overview}
+FAT-Pointers, combined with the capabilities of the CHERI (Capability Hardware Enhanced RISC Instructions) 
+architecture, introduce robust memory safety and security features by incorporating additional metadata 
+with memory pointers. This enhanced architecture utilizes concepts such as FlexPointer, 
+Range Memory Mapping (RMM), and Direct segment to manage memory effectively.
+
+Range addresses play a pivotal role within this framework, defining memory 
+regions bounded by a starting address (BASE) and an ending address (LIMIT). 
+These range addresses are encoded within FAT-pointers, allowing for precise 
+control over memory access permissions.
+
+The functionality of ranges encompasses several key aspects:
+\begin{itemize}
+\item \textbf{Creation of Physically Contiguous Memory Ranges}:
+By defining memory regions that are physically contiguous, systems can 
+achieve optimal memory access patterns, enhancing performance and efficiency.
+\item \textbf{Encoding Ranges as Bounds to the Pointer}:
+Integrating range bounds directly into FAT-pointers enables the architecture 
+to enforce memory access restrictions at the pointer level thus allowing 
+tracking of memory ranges on a pointer level.
+\item \textbf{Instrumenting Block-Based Allocators with Physically Contiguous Memory}:
+The integration of range-based memory concepts into memory allocation systems, such as block-based 
+allocators, facilitates the efficient management and utilization of physically contiguous memory blocks, 
+mitigating issues related to memory fragmentation.
+\end{itemize}
 
@@
 \section{Related work}
-Efficient memory management, particularly in the context of 
-Translation Lookaside Buffer (TLB) optimization \cite{ad-wood-2003}, has been a focal point of 
-research and development within computer architecture. Various techniques have been 
-proposed to mitigate TLB-related bottlenecks and improve overall system performance.
-
-\subsection{Huge Pages}
-This is used to map a very large region of memory to a 
-single entry. This small/large region of memory is physically
-contiguous. Most implementations of huge pages are size
-aligned, For example for the x86 architecture the huge pages 
-size are 4KB, 2MB and 1GB pages. 
-% \subsection{Tailored page sizes}
-% TODO later
-% \subsection{TLB coalescing}
-% This leverages the default OS allocator behavior to pack
-% multiple PTEs into a single TLB entry.
-
-\subsection{Segment}
-A segment can be viewed as mapping between contiguous virtual
-memory and contiguous physical memory. The property of a 
-segment allows it to be larger than a page. Direct Segment
-<paper reference> allows the user to set a single segment
-for an application. Two registers are added to mark the start
-and end of the segment. Any virtual address within this region
-can be translated by adding the fixed offset between the virtual
-and physical address.
-
-\subsection{RMM}
-RMM introduces the concept of adding an additional range table.
-For large allocations RMM eagerly allocates contiguous physical pages.
-The following allocations creates large memory ranges that are
-both virtually and physically contiguous. RMM builds on the concept
-of Direct segment <paper reference> by adding offset to translate a virtual address 
-to physical address. RMM compares address with range boundaries 
-to decide which range it belongs to. RMM queries the range table 
-ofter an L1 TLB miss.
-
-\subsection{FlexPointer}
-FlexPointer is based on the RMM<paper reference RMM> paper. FlexPointer
-does eagerly allocate pages which are physically contiguous and stores the ID to translate a virtual address 
-to physical address on the remaining unused bits on the 64 bit virtual address. 
-The paper contribution mentions shifting the TLB lookup to an earlier stage to improve
-latency of accessing the TLB entries. FlexPointer immediate queries the 
-range TLB for translations rather than the RMM paper which waits for the L1 TLB miss.
 

### 2024-05-21 papers/ISMM/FlexPointer/paper.tex
added new diagrams draw.io

@@
 significant performance improvements can be realized. This approach not only enhances 
-system security but also accelerates memory access
+system security but also accelerates memory access.
 
@@
 \subsection{Range creation}
+Ranges of memory are created based on bounds encoded to the FAT-Pointer. 
+The Chuck between the following bounds is physically contiguous.
+This is done via the FreeBSD kernel Contig memory allocator.
 
 \subsection{Fragmentation}
+The problem with standard allocators which are physically contiguous
+is that they are mostly on the
 
@@
 \section{Evaluation}
+
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}{|l|l|l|l|l|}
+  \hline
+      \textbf{Metric name} & \textbf{type of graph} & \textbf{tool used} & \textbf{x axis} & \textbf{y axis} \\ \hline
+      DTLB L1 read & line graph & Pmcstat & Time & DTLB L1 reads (each second) \\ \hline
+      DTLB L2 read & line graph & Pmcstat & Time & DTLB L2 reads (each second) \\ \hline
+      DTLB walk & line graph & Pmcstat & Time & DTLB Walks (each second) \\ \hline
+      L1 cache miss & line graph & Pmcstat & Time & L1 cache miss (each second) \\ \hline
+      Wall clock run time & bar graph & time & Benchmarks & Time \\ \hline
+      Resident memory usage & line graph & ps with rss & Time & Memory in MB \\ \hline
+      Speed ups & bar graph & time & Benchmarks & Time \\ \hline
+  \end{tabular}
+\end{table}
 

### 2024-05-24 papers/ISMM/FlexPointer/paper.tex
added more base content

@@
 \subsection{Overview}
+
 FAT-Pointers, combined with the capabilities of the CHERI (Capability Hardware Enhanced RISC Instructions) 
@@
 
-\subsection{Range creation}
-Ranges of memory are created based on bounds encoded to the FAT-Pointer. 
-The Chuck between the following bounds is physically contiguous.
-This is done via the FreeBSD kernel Contig memory allocator.
+\begin{minipage}[t]{0.4\linewidth}
+  \includegraphics[width=2\textwidth]{diagrams/HighOverviewArchitecture24.png}
+\end{minipage}
+
+\subsection{Range creation and huge pages}
+\begin{minipage}[t]{0.4\linewidth}
+  \includegraphics[width=2\textwidth]{diagrams/AllocationOverview24.png}
+\end{minipage}
+
+% Ranges of memory are created based on bounds encoded to the FAT-Pointer based on the CHERI 128 bit 
+% bounds compressed scheme. The Chuck between the specified upper and lower bounds are always physically
+% contiguous. In the following implementation an arbitrary size huge page is initially allocated and within 
+% this huge page custom size memory is allocated using a custom written mmap function which overwrites the existing block 
+% based mmap function. Once memory is physically allocated using the custom mmap function call then bounds are set to it for tracking 
+% the block of memory instead of using the TLB.
+
+In this implementation, memory ranges are established using bounds encoded within the FAT-pointer, adhering 
+to the CHERI 128-bit bounds compression scheme. The memory chunk defined by the upper and lower bounds is 
+always physically contiguous. Initially, a huge page of arbitrary size is allocated. Within this huge page, 
+custom-sized memory segments are allocated using a custom-designed mmap function, which overrides the existing 
+block-based mmap function. Once the memory is physically allocated through this custom mmap function, bounds 
+are set to track the memory block, eliminating the need for traditional TLB usage for this purpose. Traditional TLB usage 
+involves maintaining numerous TLB entries, often supplemented by an L2 TLB and other hierarchical structures, 
+to translate virtual addresses to physical addresses. This approach requires multiple entries to handle various 
+memory segments, leading to increased overhead and complexity in address translation. Conversely, 
+the current approach streamlines this process by using a single TLB entry to translate multiple
+ addresses within a contiguous memory range. This reduces the number of required TLB entries, 
+ simplifying the translation process and improving efficiency. By consolidating address translations 
+ into a single TLB entry, this method minimizes the overhead associated with managing numerous TLB entries 
+ and leverages the bounds encoded within the FAT-pointer for efficient memory tracking and access. 
+ This approach allows for precise and efficient memory management within the allocated huge page.
+
+%  The figure mentioned above demonstrates a simple use-case were the dark pink line refers to a huge page and 
+%  the orange and blue lines are 2 equivalent to 2 Malloc calls allocating memory in different regions which in turn
+%  emulates a block based memory allocator within a huge page using the bounds encoded in the FAT-Pointer.
+\smallskip\noindent
+The figure above illustrates a straightforward use-case in which the dark pink line represents a single, 
+large contiguous memory area, or huge page. Within this huge page, the orange and blue lines indicate 
+two separate memory allocations equivalent to invoking malloc twice to allocate memory in distinct regions. 
+This scenario simulates a block-based memory allocator operating within the confines of the huge page. 
+The allocations leverage the bounds encoded in the FAT-pointer, ensuring tracking and efficient 
+management of the allocated memory regions. By using the FAT-pointer bounds, this method maintains the 
+integrity and contiguity of the allocated blocks within the huge page.
+
+% This is done via the FreeBSD kernel Contiguous memory allocator.
 
@@
 is that they are mostly on the
-
-\subsection{Allocation with huge pages}
+% \subsection{Allocation with huge pages}
+
+\subsection{Software Stack}
+\begin{minipage}[t]{0.4\linewidth}
+  \includegraphics[width=2\textwidth]{diagrams/SoftwareStack24.png}
+\end{minipage}
 

### 2024-06-04 papers/ISMM/FlexPointer/paper.tex
saving current changes

@@
 %% complete the rights form.
-\setcopyright{acmlicensed}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{XXXXXXX.XXXXXXX}
+% \setcopyright{acmlicensed}
+% \copyrightyear{2018}
+% \acmYear{2018}
+% \acmDOI{XXXXXXX.XXXXXXX}
 
@@
 %% These commands are for a JOURNAL article.
-\acmJournal{JACM}
-\acmVolume{37}
-\acmNumber{4}
-\acmArticle{111}
-\acmMonth{8}
+% \acmJournal{JACM}
+% \acmVolume{37}
+% \acmNumber{4}
+% \acmArticle{111}
+% \acmMonth{8}
 
@@
 % - Add references for FlexPointer, Range Memory Mapping (RMM), Direct Segment and Huge Pages
-\subsection{Background}
+\subsection{TLB based approaches}
 Efficient memory management, particularly in the context of 
@@
 single entry. This small/large region of memory is physically
-contiguous. Most implementations of huge pages are size
+contiguous. Most implementations of huge pages \cite{panwar_hawkeye_2019} are size
 aligned, For example for the x86 architecture the huge pages 
@@
 memory and contiguous physical memory. The property of a 
-segment allows it to be larger than a page. Direct Segment
-<paper reference> allows the user to set a single segment
+segment allows it to be larger than a page. Direct Segment allows the user to set a single segment
 for an application. Two registers are added to mark the start
@@
 
-\subsubsection{RMM:}
-RMM introduces the concept of adding an additional range table.
+\subsubsection{Range Memory Mapping (RMM):}
+RMM\cite{karakostas_redundant_2015} introduces the concept of adding an additional range table.
 For large allocations RMM eagerly allocates contiguous physical pages.
@@
 both virtually and physically contiguous. RMM builds on the concept
-of Direct segment <paper reference> by adding offset to translate a virtual address 
+of Direct segment by adding offset to translate a virtual address 
 to physical address. RMM compares address with range boundaries 
@@
 \subsubsection{FlexPointer:}
-FlexPointer is based on the RMM<paper reference RMM> paper. FlexPointer
+FlexPointer\cite{chen_flexpointer_2023} is based on the RMM\cite{karakostas_redundant_2015} paper. FlexPointer
 does eagerly allocate pages which are physically contiguous and stores the ID to translate a virtual address 
@@
 
+\subsection{CHERI}
+A capability functions as a token that provides the holder with the authority to 
+execute specific actions. By carefully managing who possesses these capabilities, 
+it is possible to enforce security measures, such as ensuring that a particular
+section of software can only read from a designated range of memory addresses.
+
+The concept of capabilities has a rich history in computer science, tracing 
+back to early systems designed to enhance security and manage resources effectively.
+For instance, foundational work discussed in sources like [7] offers a comprehensive 
+narrative on the evolution of capability architectures. This historical perspective 
+can be further enriched by incorporating insights from more recent studies, 
+such as those found in [11].
+
+CHERI (Capability Hardware Enhanced RISC Instructions) represents a modern embodiment of this 
+long-standing idea. It introduces more granular control over permissions, allowing for finer 
+distinctions in what actions can be performed and by whom. Moreover, CHERI is designed to integrate 
+seamlessly with contemporary processor instruction sets, ensuring that these advanced security 
+features can be implemented on modern hardware platforms. This adaptation not only revitalizes 
+the capability concept but also significantly enhances its applicability and effectiveness 
+in current computing environments.
+
 \section{FAT-Pointer based range addresses}
-This experiment exploits the FAT pointer to enable faster
+% This experiment exploits the FAT pointer to enable faster
 
@@
 % - Add references for FlexPointer, Range Memory Mapping (RMM) and Direct segment
-\subsection{Overview}
+% \subsection{Overview}
 
@@
 with memory pointers. This enhanced architecture utilizes concepts such as FlexPointer, 
-Range Memory Mapping (RMM), and Direct segment to manage memory effectively.
+Range Memory Mapping (RMM) to manage memory effectively.
 
 Range addresses play a pivotal role within this framework, defining memory 
-regions bounded by a starting address (BASE) and an ending address (LIMIT). 
+regions bounded by a starting address (Upper) and an ending address (Lower). 
 These range addresses are encoded within FAT-pointers, allowing for precise 
-control over memory access permissions.
+control over memory regions.
 
@@
 
-\begin{minipage}[t]{0.4\linewidth}
-  \includegraphics[width=2\textwidth]{diagrams/HighOverviewArchitecture24.png}
-\end{minipage}
+% \begin{minipage}[t]{0.4\linewidth}
+\begin{figure}[h]
+  \includegraphics[width=0.8\textwidth]{diagrams/HighOverviewArchitecture24.png}
+  \caption{High overview architecture}
+  \label{fig:HighOverviewArchitecture}
+% \end{minipage}
+\end{figure}
+
+% The figure above demonstrates the approach taken for using CHERI 
+% 128bit FAT pointer scheme to allow a blocked based behavior on 
+% on physically contiguous memory which is on the right against the 
+% regular mmap approach which further elaborated in section (). The 
+% green highlighted refers to the excess space available between 
+% the 48th and 64th bit which can be used to store more meta-data which 
+% is elaborated in the future work section().
+
+Figure \ref{fig:HighOverviewArchitecture} illustrates the methodology employed to leverage the CHERI 
+128-bit FAT-pointer scheme for facilitating block-based memory management
+ on physically contiguous memory, which is depicted on the right side of the figure. 
+ This technique contrasts with the conventional mmap approach, the details of which 
+ are elaborated in section ("To be added later").
+
+In figure \ref{fig:HighOverviewArchitecture}, the green-highlighted section marks the unused space between the 48th and 64th bits
+within the FAT-pointer. This area of unused bits presents an opportunity to store additional metadata,
+potentially enhancing the capabilities of the memory management system. The potential applications of 
+this extra space are discussed in the future work section ("To be added later"), 
+where we explore how this additional metadata storage could be used to further optimize memory allocation.
+
+% By employing the CHERI 128-bit FAT-pointer scheme, the approach depicted aims to streamline the management of memory blocks, ensuring they are physically contiguous.
+This is in contrast to the traditional mmap approach, which typically does not guarantee physical contiguity of allocated memory regions.
 
 \subsection{Range creation and huge pages}
-\begin{minipage}[t]{0.4\linewidth}
-  \includegraphics[width=2\textwidth]{diagrams/AllocationOverview24.png}
-\end{minipage}
+% \begin{minipage}[t]{0.4\linewidth}
+\begin{figure}[h]
+  \includegraphics[width=0.8\textwidth]{diagrams/AllocationOverview24.png}
+  \caption{Range of memory}
+  \label{fig:RangeOfMemory}
+\end{figure}
+% \end{minipage}
 
@@
 In this implementation, memory ranges are established using bounds encoded within the FAT-pointer, adhering 
-to the CHERI 128-bit bounds compression scheme. The memory chunk defined by the upper and lower bounds is 
+to the CHERI 128-bit bounds compression scheme\cite{woodruff_cheri_2019}. The memory chunk defined by the upper and lower bounds is 
 always physically contiguous. Initially, a huge page of arbitrary size is allocated. Within this huge page, 
@@
 \smallskip\noindent
-The figure above illustrates a straightforward use-case in which the dark pink line represents a single, 
+Figure \ref{fig:RangeOfMemory} illustrates a straightforward use-case in which the dark pink line represents a single, 
 large contiguous memory area, or huge page. Within this huge page, the orange and blue lines indicate 
@@
 
-\subsection{Fragmentation}
-The problem with standard allocators which are physically contiguous
-is that they are mostly on the
+% \subsection{Fragmentation}
+% % The problem with standard allocators which are physically contiguous
+% % is that they are mostly on the
+% todo
 % \subsection{Allocation with huge pages}
@@
 \subsection{Software Stack}
-\begin{minipage}[t]{0.4\linewidth}
-  \includegraphics[width=2\textwidth]{diagrams/SoftwareStack24.png}
-\end{minipage}
+\begin{figure}[h]
+% \begin{minipage}[t]{0.4\linewidth}
+\includegraphics[width=0.8\textwidth]{diagrams/SoftwareStack24.png}
+\caption{Overview of the software stack}
+\label{fig:SoftwareStack}
+% \end{minipage}
+\end{figure}
+
+% The Software stack consists of CHERIBSD as the base operating system due to official 
+% support by ARM to the Morello's performance counters. As mentioned in the figure above 
+% there is a C program that is linked to the prototype memory allocator or allocators benchmarked 
+% against as mentioned in section (x) as either a Shared object file at compile time or as a header 
+% file for smaller memory allocators. The modified mmap function call which is designed to be physically 
+% contiguous is linked to the contigmem driver which is modified from the DPDK library (reference).
+% The contigmem driver is loaded on boot time and reserves arbitrary size of a huge page which is
+% set based on the experiment conducted.
+
+The software stack is based on CHERIBSD, selected because ARM officially supports Morello's performance 
+counters on this operating system. As illustrated in the figure \ref{fig:SoftwareStack}, the setup includes a C program that 
+is linked to the prototype memory allocator or to various memory allocators being benchmarked, as described 
+in section ("Evaluation section"). This linkage can occur in two ways: either as a shared object file during compile time 
+for larger allocators, or as a header file for smaller allocators, ensuring flexibility and efficiency 
+in memory management.
+
+The custom mmap function, tailored to ensure physically contiguous memory allocation, is a key component 
+of this system. This function is linked to the contigmem driver, which has been modified from the DPDK library 
+to meet the specific needs of this implementation. The contigmem driver is essential for managing large contiguous 
+memory blocks and is loaded during the system boot process. It reserves a huge page of arbitrary size, with the 
+size parameter set based on the requirements of the conducted experiments.
+
+This integration ensures that the memory allocation process is optimized for performance, leveraging the contiguity 
+of memory blocks and the capabilities provided by the CHERI architecture and the Morello platform. By using the 
+contigmem driver and the custom mmap function, the system achieves efficient memory allocation and tracking, 
+crucial for the high-performance needs of the application.
 
 \section{Evaluation}
+To evaluate the performance of FAT-Pointer based range addresses a sample implementation we used
+the morello board with CheriBSD's Benchmark ABI compilation mode for accurate performance recordings. 
+The evaluation is to identify CheriBSD's default memory allocator SnMalloc against the prototype memory 
+allocator using the contribution of this paper in terms of: 
+To assess the performance of FAT-Pointer-based range addressing in the sample implementation, we utilized the 
+Morello board running CheriBSD in Benchmark ABI compilation mode to ensure precise performance measurements. 
+The evaluation focuses on comparing CheriBSD's default memory allocator, SnMalloc, against the prototype 
+memory allocator developed in this study, with particular attention to the following aspects:
 
@@
   \hline
-      \textbf{Metric name} & \textbf{type of graph} & \textbf{tool used} & \textbf{x axis} & \textbf{y axis} \\ \hline
+      Metric name & type of graph & tool used & x axis & y axis \\ \hline
       DTLB L1 read & line graph & Pmcstat & Time & DTLB L1 reads (each second) \\ \hline
@@
       Wall clock run time & bar graph & time & Benchmarks & Time \\ \hline
-      Resident memory usage & line graph & ps with rss & Time & Memory in MB \\ \hline
-      Speed ups & bar graph & time & Benchmarks & Time \\ \hline
   \end{tabular}
@@
 
-\section{Limitations}
-
-\section{Related work}
-
-\section{Summary}
+\subsection{Benchmarks used}:
+To conduct the evaluations, we utilized the COZ benchmark suite, a well-regarded tool specifically designed 
+to measure and analyze performance improvements in concurrent programs. The COZ benchmark suite provides a
+robust framework for identifying bottlenecks and evaluating the performance impact of various optimization
+techniques. By leveraging COZ, developers can gain precise insights into the efficiency and scalability of
+their concurrent code, making it an ideal choice for rigorous performance analysis.
+
+From the extensive set of benchmarks provided by COZ, we selected four representative C programs. 
+These programs were chosen based on their relevance to common concurrent programming patterns and
+their ability to effectively demonstrate the strengths and weaknesses of different optimization 
+strategies. The selected programs cover a range of concurrency scenarios, ensuring a comprehensive
+evaluation of performance improvements.
+
+By implementing these modifications, we ensured that the selected C programs not only adhered to
+CHERI's security model but also maintained their functional and performance characteristics. 
+This allowed us to effectively use the COZ benchmark suite to analyze the performance in a CHERI-enhanced environment.
+
+\begin{figure}[h]
+  \includegraphics[width=0.8\textwidth]{diagrams/expirement-runs.png}
+\end{figure}
+
+% \begin{itemize} % Coz C programs
+%   \item Kmeans
+%   \item Histogram
+%   \item Matrix multiply
+% \end{itemize}
+
+\subsection{Future work}
+% The future plan is to transition from the current experiment, which involves working on the ARM architecture on the ARM Morello board. 
+% The current limitation is that all memory reads must go through the TLB for translations. The future plan involves storing 
+% the offset directly on the pointer and using the bounds in CHERI to enable block-based allocator behavior. This phase of the 
+% experiment is intended to be conducted on the RISC-V implementation of CHERI, known as Tooba.
+
+% In the RISC-V implementation, the hardware Verilog design will be modified to allow bypassing the TLB. Once this concept is 
+% integrated into the RISC-V Verilog implementation, the OS layer will be changed to a single-address-space operating system, 
+% where there is no distinction between user space and kernel space. In this implementation, the kernel allocator will be the 
+% same as the user space allocator since both can utilize a single contiguous chunk of memory.
+The current experimental setup on the ARM Morello board is constrained by the requirement that all memory reads must 
+pass through the Translation Lookaside Buffer (TLB) for address translation. This necessitates frequent TLB lookups, potentially 
+leading to performance bottlenecks. The planned future work aims to address this by leveraging CHERI 
+(Capability Hardware Enhanced RISC Instructions) extensions on the RISC-V architecture, specifically using the 
+Tooba implementation.
+
+\subsubsection{Storing Offsets Directly on Pointers}
+In the current ARM Morello setup, address translations rely on the TLB.
+The future approach on RISC-V Tooba involves storing the offset directly within the pointer.
+This is possible due to CHERI's capability model, which supports fine-grained memory protection and can encode bounds within pointers.
+Utilizing Bounds in CHERI for Block-Based Allocation:
+
+CHERI capabilities allow pointers to carry metadata about memory bounds, providing hardware-enforced memory safety.
+By encoding the offset and bounds within the pointer, the system can directly access memory without needing intermediate translations via the TLB.
+This enables the implementation of a block-based allocator that can efficiently manage memory allocations and deallocations within defined bounds.
+Bypassing the TLB in RISC-V Tooba.
+\subsubsection{Hardware Modifications}:
+The Verilog design of the RISC-V processor will be modified to allow certain memory operations to bypass the TLB.
+This means that when a pointer with encoded offset and bounds is used, the system can directly compute the physical address from the capability information.
+This modification reduces the dependency on the TLB, decreasing latency and improving performance, especially for frequent memory operations.
+Transition to a Single-Address-Space Operating System (SASOS).
+\subsubsection{Concept of SASOS}:
+In traditional operating systems, there is a clear separation between user space and kernel space. This separation is enforced by memory protection mechanisms and address translation through the TLB.
+In a Single-Address-Space Operating System, this distinction is removed. Both user applications and the kernel share the same contiguous address space.
+\subsubsection{Advantages of SASOS with CHERI}:
+\begin{itemize}
+  \item Simplified Memory Management : Without the need to switch between user and kernel spaces, memory management becomes simpler and more efficient.
+The kernel allocator can be the same as the user space allocator, operating on a single, contiguous chunk of memory.
+  \item Unified Allocator: The unified memory allocator can efficiently manage memory for both kernel and user applications, leveraging CHERI's capability-based protection to prevent unauthorized access.
+This reduces overhead and potential fragmentation issues associated with maintaining separate memory spaces.
+\end{itemize}
+
+% Explain contig module in detail
+
+% Graphs
+
+  % \begin{table}[!ht]
+  %   \centering
+  %   \begin{tabular}{|l|l|l|l|l|}
+  %   \hline
+  %       \textbf{Metric name} & \textbf{type of graph} & \textbf{tool used} & \textbf{x axis} & \textbf{y axis} \\ \hline
+  %       DTLB L1 read & line graph & Pmcstat & Time & DTLB L1 reads (each second) \\ \hline
+  %       DTLB L2 read & line graph & Pmcstat & Time & DTLB L2 reads (each second) \\ \hline
+  %       DTLB walk & line graph & Pmcstat & Time & DTLB Walks (each second) \\ \hline
+  %       L1 cache miss & line graph & Pmcstat & Time & L1 cache miss (each second) \\ \hline
+  %       Wall clock run time & bar graph & time & Benchmarks & Time \\ \hline
+  %       Resident memory usage & line graph & ps with rss & Time & Memory in MB \\ \hline
+  %       Speed ups & bar graph & time & Benchmarks & Time \\ \hline
+  %   \end{tabular}
+  % \end{table}
+
+  % \section{Limitations}
+
+  % \section{Related work}
+
+  % \section{Summary}
 
@@
 
-\begin{acks}
-  To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
+% \begin{acks}
+%   To Robert, for the bagels and explaining CMYK and color spaces.
+% \end{acks}
 

### 2024-09-05 papers/EuroSys/Paper/paper.tex
latest changes

--- 2024-05-24 papers/ISMM/FlexPointer/paper.tex
@@
 %%
-%% This is file `sample-acmsmall-submission.tex',
+%% This is file `sample-sigconf-authordraft.tex',
 %% generated with the docstrip utility.
@@
 %%
-%% samples.dtx  (with options: `acmsmall-submission')
+%% samples.dtx  (with options: `all,proceedings,bibtex,authordraft')
 %%
@@
 %% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-acmsmall-submission.tex.
+%% with new filenames distinct from sample-sigconf-authordraft.tex.
 %%
@@
 %%
-\documentclass[acmsmall,screen,review]{acmart}
-
-% \usepackage[style=authoryear, useprefix = false]{biblatex}
+\documentclass[sigconf,authordraft]{acmart}
+\usepackage{listings}
+\lstset{basicstyle=\small\ttfamily,columns=fullflexible}
 
@@
 
-%%
-%% These commands are for a JOURNAL article.
-\acmJournal{JACM}
-\acmVolume{37}
-\acmNumber{4}
-\acmArticle{111}
-\acmMonth{8}
+%% These commands are for a PROCEEDINGS abstract or paper.
+\acmConference[Conference acronym 'XX]{Make sure to enter the correct
+  conference title from your rights confirmation emai}{June 03--05,
+  2018}{Woodstock, NY}
+%%
+%%  Uncomment \acmBooktitle if the title of the proceedings is different
+%%  from ``Proceedings of ...''!
+%%
+%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
+%%  June 03--05, 2018, Woodstock, NY}
+\acmISBN{978-1-4503-XXXX-X/18/06}
 
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{FAT-Pointer based range addresses}
+\title{FAT Pointer based range addresses}
 
@@
 % \authornote{Both authors contributed equally to this research.}
+% \email{as251@hw.ac.uk}
+% \orcid{1234-5678-9012}
+% \author{G.K.M. Tobin}
+\authornotemark[1]
 \email{as251@hw.ac.uk}
-\orcid{1234-5678-9012}
-% \author{G.K.M. Tobin}
-% \authornotemark[1]
-% \email{webmaster@marysville-ohio.com}
 \affiliation{%
-  \institution{Heriot Watt University}
-  % \streetaddress{P.O. Box 1212}
-  % \city{Dublin}
-  % \state{Ohio}
-  \country{UK}
-  % \postcode{43017-6221}
+  \institution{Heriot Watt}
+  \city{Edinburgh}
+  \state{Scotland}
+  \country{United Kingdom}
 }
@@
 %   \institution{The Th{\o}rv{\"a}ld Group}
-%   \streetaddress{1 Th{\o}rv{\"a}ld Circle}
 %   \city{Hekla}
@@
 %  \institution{Rajiv Gandhi University}
-%  \streetaddress{Rono-Hills}
 %  \city{Doimukh}
@@
 %   \institution{Tsinghua University}
-%   \streetaddress{30 Shuangqing Rd}
 %   \city{Haidian Qu}
@@
 %   \institution{Palmer Research Laboratories}
-%   \streetaddress{8600 Datapoint Drive}
 %   \city{San Antonio}
 %   \state{Texas}
-%   \country{USA}
-%   \postcode{78229}}
+%   \country{USA}}
 % \email{cpalmer@prl.com}
@@
 \begin{abstract}
-  % Draft 1
-  % The gap between application workloads and capacity of TLB is on the 
-  % rise. Previous work exploits this by physically contiguous 
-  % memory. Capability-based addressing in the CHERI architecture is 
-  % designed to improve hardware-level system security.
-  % These security mechanisms designed in place can also 
-  % behave as accelerators to standard user-space memory allocators. 
-  % The property of CHERI which is to use FAT-Pointers to store
-  % the upper and lower bounds can also be represented as ranges of 
-  % memory addresses which are physically contiguous. 
-  % <Talking about the results>.
-  % Draft 2
 The increasing disparity between application workloads and the capacity of Translation Lookaside Buffers (TLB) 
@@
 %% Please copy and paste the code instead of the example below.
-%%
+% %%
 % \begin{CCSXML}
@@
 %   Your, Paper}
+%% A "teaser" image appears between the author and affiliation
+%% information and the body of the document, and typically spans the
+%% page.
+% \begin{teaserfigure}
+%   \includegraphics[width=\textwidth]{sampleteaser}
+%   \caption{Seattle Mariners at Spring Training, 2010.}
+%   \Description{Enjoying the baseball game from the third-base
+%   seats. Ichiro Suzuki preparing to bat.}
+%   \label{fig:teaser}
+% \end{teaserfigure}
 
@@
 % \received[accepted]{5 June 2009}
-
-% Sample citation
-% \cite{ad-wood-2003}
 
@@
 However, as applications grow in size and complexity, the capacity of TLBs often struggles to 
-keep pace, leading to performance bottlenecks. To address this challenge, researchers have 
+keep pace, leading to performance bottlenecks\cite{mittal_survey_2017}. To address this challenge, researchers have 
 turned to innovative solutions, one of which involves harnessing the benefits of huge pages.
@@
 significant performance improvements can be realized. This approach not only enhances 
-system security but also accelerates memory access.
-
-% TODO: 
-% - Add references for FlexPointer, Range Memory Mapping (RMM), Direct Segment and Huge Pages
-\subsection{Background}
-Efficient memory management, particularly in the context of 
-Translation Lookaside Buffer (TLB) optimization, has been a focal point of 
-research and development within computer architecture. Various techniques have been 
-proposed to mitigate TLB-related bottlenecks and improve overall system performance.
-
-\subsubsection{Huge Pages:}
-This is used to map a very large region of memory to a 
-single entry. This small/large region of memory is physically
-contiguous. Most implementations of huge pages are size
-aligned, For example for the x86 architecture the huge pages 
-size are 4KB, 2MB and 1GB pages. 
-% \subsection{Tailored page sizes}
-% TODO later
-% \subsection{TLB coalescing}
-% This leverages the default OS allocator behavior to pack
-% multiple PTEs into a single TLB entry.
-
-\subsubsection{Segment:}
-A segment can be viewed as mapping between contiguous virtual
-memory and contiguous physical memory. The property of a 
-segment allows it to be larger than a page. Direct Segment
-<paper reference> allows the user to set a single segment
-for an application. Two registers are added to mark the start
-and end of the segment. Any virtual address within this region
-can be translated by adding the fixed offset between the virtual
-and physical address.
-
-\subsubsection{RMM:}
-RMM introduces the concept of adding an additional range table.
-For large allocations RMM eagerly allocates contiguous physical pages.
-The following allocations creates large memory ranges that are
-both virtually and physically contiguous. RMM builds on the concept
-of Direct segment <paper reference> by adding offset to translate a virtual address 
-to physical address. RMM compares address with range boundaries 
-to decide which range it belongs to. RMM queries the range table 
-ofter an L1 TLB miss.
-
-\subsubsection{FlexPointer:}
-FlexPointer is based on the RMM<paper reference RMM> paper. FlexPointer
-does eagerly allocate pages which are physically contiguous and stores the ID to translate a virtual address 
-to physical address on the remaining unused bits on the 64 bit virtual address. 
-The paper contribution mentions shifting the TLB lookup to an earlier stage to improve
-latency of accessing the TLB entries. FlexPointer immediate queries the 
-range TLB for translations rather than the RMM paper which waits for the L1 TLB miss.
-
-\section{FAT-Pointer based range addresses}
-This experiment exploits the FAT pointer to enable faster
-
-% TODO: 
-% - Add references for FlexPointer, Range Memory Mapping (RMM) and Direct segment
-\subsection{Overview}
-
-FAT-Pointers, combined with the capabilities of the CHERI (Capability Hardware Enhanced RISC Instructions) 
+system security but also accelerates memory access. The following below are research questions 
+we are addressing:
+\newline
+
+\begin{enumerate}
+    \item How does the utilization of bounds for tracking memory allocations, in addition to security purposes, affect the 
+    run times and Translation Lookaside Buffer (TLB) miss rates in modern computing systems?
+    \item How does the implementation of bounds for seeking through physically contiguous memory influence the complexity and 
+    efficiency of standard memory allocators, particularly those with advanced features such as transparent 
+    huge pages, and what are the implications for system performance in terms of execution speed, memory access 
+    latency, and resource utilization?
+\end{enumerate}
+
+\section{FAT Pointer based range addresses}
+FAT-Pointers based range addresses, combined with the capabilities of the CHERI (Capability Hardware Enhanced RISC Instructions) 
 architecture, introduce robust memory safety and security features by incorporating additional metadata 
 with memory pointers. This enhanced architecture utilizes concepts such as FlexPointer, 
-Range Memory Mapping (RMM), and Direct segment to manage memory effectively.
+Range Memory Mapping (RMM) to manage memory effectively.
 
 Range addresses play a pivotal role within this framework, defining memory 
-regions bounded by a starting address (BASE) and an ending address (LIMIT). 
+regions bounded by a starting address (Upper) and an ending address (Lower). 
 These range addresses are encoded within FAT-pointers, allowing for precise 
-control over memory access permissions.
+control over memory regions.
 
@@
 
-\begin{minipage}[t]{0.4\linewidth}
-  \includegraphics[width=2\textwidth]{diagrams/HighOverviewArchitecture24.png}
-\end{minipage}
+\begin{figure}[h]
+  \includegraphics[width=0.4\textwidth]{diagram/HighOverviewArchitecture24.png}
+  \caption{High overview architecture}
+  \label{fig:HighOverviewArchitecture}
+% \end{minipage}
+\end{figure}
+
+Figure \ref{fig:HighOverviewArchitecture} illustrates the methodology employed to leverage the CHERI 
+128-bit FAT-pointer scheme for facilitating block-based memory management
+on physically contiguous memory, which is depicted on the right side of the figure. 
+This technique contrasts with the conventional mmap approach.
+
+In figure \ref{fig:HighOverviewArchitecture}, the green-highlighted section marks the unused space between the 48th and 64th bits
+within the FAT-pointer. This area of unused bits presents an opportunity to store additional metadata,
+potentially enhancing the capabilities of the memory management system. 
+Here we explore how this additional metadata storage could be used to further optimize memory allocation.
 
 \subsection{Range creation and huge pages}
-\begin{minipage}[t]{0.4\linewidth}
-  \includegraphics[width=2\textwidth]{diagrams/AllocationOverview24.png}
-\end{minipage}
-
-% Ranges of memory are created based on bounds encoded to the FAT-Pointer based on the CHERI 128 bit 
-% bounds compressed scheme. The Chuck between the specified upper and lower bounds are always physically
-% contiguous. In the following implementation an arbitrary size huge page is initially allocated and within 
-% this huge page custom size memory is allocated using a custom written mmap function which overwrites the existing block 
-% based mmap function. Once memory is physically allocated using the custom mmap function call then bounds are set to it for tracking 
-% the block of memory instead of using the TLB.
-
+\begin{figure}[h]
+  \includegraphics[width=0.4\textwidth]{diagram/AllocationOverview24.png}
+  \caption{Range of memory}
+  \label{fig:RangeOfMemory}
+\end{figure}
 In this implementation, memory ranges are established using bounds encoded within the FAT-pointer, adhering 
-to the CHERI 128-bit bounds compression scheme. The memory chunk defined by the upper and lower bounds is 
+to the CHERI 128-bit bounds compression scheme\cite{woodruffcheri2019}. The memory chunk defined by the upper and lower bounds is 
 always physically contiguous. Initially, a huge page of arbitrary size is allocated. Within this huge page, 
@@
 
-%  The figure mentioned above demonstrates a simple use-case were the dark pink line refers to a huge page and 
-%  the orange and blue lines are 2 equivalent to 2 Malloc calls allocating memory in different regions which in turn
-%  emulates a block based memory allocator within a huge page using the bounds encoded in the FAT-Pointer.
 \smallskip\noindent
-The figure above illustrates a straightforward use-case in which the dark pink line represents a single, 
+Figure \ref{fig:RangeOfMemory} illustrates a straightforward use-case in which the dark pink line represents a single, 
 large contiguous memory area, or huge page. Within this huge page, the orange and blue lines indicate 
@@
 
-% This is done via the FreeBSD kernel Contiguous memory allocator.
-
-\subsection{Fragmentation}
-The problem with standard allocators which are physically contiguous
-is that they are mostly on the
-% \subsection{Allocation with huge pages}
-
 \subsection{Software Stack}
-\begin{minipage}[t]{0.4\linewidth}
-  \includegraphics[width=2\textwidth]{diagrams/SoftwareStack24.png}
-\end{minipage}
-
-\section{Evaluation}
-
-\begin{table}[!ht]
-  \centering
-  \begin{tabular}{|l|l|l|l|l|}
-  \hline
-      \textbf{Metric name} & \textbf{type of graph} & \textbf{tool used} & \textbf{x axis} & \textbf{y axis} \\ \hline
-      DTLB L1 read & line graph & Pmcstat & Time & DTLB L1 reads (each second) \\ \hline
-      DTLB L2 read & line graph & Pmcstat & Time & DTLB L2 reads (each second) \\ \hline
-      DTLB walk & line graph & Pmcstat & Time & DTLB Walks (each second) \\ \hline
-      L1 cache miss & line graph & Pmcstat & Time & L1 cache miss (each second) \\ \hline
-      Wall clock run time & bar graph & time & Benchmarks & Time \\ \hline
-      Resident memory usage & line graph & ps with rss & Time & Memory in MB \\ \hline
-      Speed ups & bar graph & time & Benchmarks & Time \\ \hline
-  \end{tabular}
-\end{table}
-
-\section{Limitations}
+The software stack is based on CHERIBSD, selected because ARM officially supports Morello's performance 
+counters on this operating system. As illustrated in the figure \ref{fig:SoftwareStack}, the setup includes a C program that 
+is linked to the prototype memory allocator or to various memory allocators being benchmarked. This linkage can occur in two ways: either as a shared object file during compile time 
+for larger allocators, or as a header file for smaller allocators, ensuring flexibility and efficiency 
+in memory management.
+\newline
+
+This integration ensures that the memory allocation process is optimized for performance, leveraging the contiguity 
+of memory blocks and the capabilities provided by the CHERI architecture and the Morello platform. By using the 
+contigmem driver and the custom mmap function, the system achieves efficient memory allocation and tracking, 
+crucial for the high-performance needs of the application.
+
+\subsection{Contigmem driver from DPDK}
+The custom mmap function, tailored to ensure physically contiguous memory allocation, is a key component 
+of this system. This function is linked to the contigmem driver, which has been modified from the DPDK\cite{bidpdk-based2016} library 
+to meet the specific needs of this implementation. The contigmem driver is essential for managing large contiguous 
+memory blocks and is loaded during the system boot process. It reserves a huge page of arbitrary size, with the 
+size parameter set based on the requirements of the conducted experiments.
+
+\begin{lstlisting}[language=C, caption=Contigmem driver , label=ContigInit]
+
+  MALLOC_DEFINE(M_CONTIGMEM, "contigmem", 
+  "contigmem(4) allocations");
+
+  static int contigmem_modevent(module_t mod, 
+  int type, void *arg)
+  {
+    int error = 0;
+
+    switch (type) {
+    case MOD_LOAD:
+      error = contigmem_load();
+      break;
+    case MOD_UNLOAD:
+      error = contigmem_unload();
+      break;
+    default:
+      break;
+    }
+
+    return error;
+  }
+
+  ....
+
+DECLARE_MODULE(contigmem, contigmem_mod, 
+SI_SUB_DRIVERS, SI_ORDER_ANY);
+MODULE_VERSION(contigmem, 1);
+
+static struct cdevsw contigmem_ops = {
+	.d_name         = "contigmem",
+	.d_version      = D_VERSION,
+	.d_flags        = D_TRACKCLOSE,
+	.d_mmap_single  = contigmem_mmap_single,
+	.d_open         = contigmem_open,
+	.d_close        = contigmem_close,
+};
+
+static int
+contigmem_load()
+{
+	....
+
+	for (i = 0; i < contigmem_num_buffers; i++) {
+		addr = contigmalloc(contigmem_buffer_size, 
+           M_CONTIGMEM, M_ZERO,
+		   0, BUS_SPACE_MAXADDR, 
+           contigmem_buffer_size, 0);
+	....
+	}
+
+    ....
+
+error:
+	for (i = 0; i < contigmem_num_buffers; i++) {
+		if (contigmem_buffers[i].addr != NULL) {
+			contigfree(contigmem_buffers[i].addr,
+				contigmem_buffer_size, M_CONTIGMEM);
+			contigmem_buffers[i].addr = NULL;
+		}
+		....
+	}
+
+	return error;
+}
+
+\end{lstlisting}
+
+When the contigmem\_load function is called, either during boot or when the Kernel module is loaded, it pre-allocates 
+a segment of physically contiguous memory. This approach differs from FlexPointer\cite{chenflexpointer2023}, 
+which allocates physically contiguous memory eagerly. The contigmem\_load function allocates memory using contigmalloc, 
+which allocates physically contiguous memory initialized to zero. The cdevsw struct refers to function 
+calls which would be overwritten on loading the driver. In the code snippet above
+the mmap function would be overwritten with contigmem\_mmap\_single if the following driver is opened and truncated
+as shown in Code snippet. 
+\newline
+
+In the code snippet the cdev\_pager\_ops refers to the operations which will be overwritten 
+when called with mmap such as overwriting page faults.
+
+% \begin{lstlisting}[language=C, caption=Contigmem driver mmap , label=ContigMmap]
+
+%   static struct cdev_pager_ops contigmem_cdev_pager_ops = {
+%     .cdev_pg_ctor = contigmem_cdev_pager_ctor,
+%     .cdev_pg_dtor = contigmem_cdev_pager_dtor,
+%     .cdev_pg_fault = contigmem_cdev_pager_fault,
+%   };
+
+%   static int
+%   contigmem_mmap_single(struct cdev *cdev, vm_ooffset_t 
+%   *offset, vm_size_t size, struct vm_object **obj, int nprot)
+%   {
+%       ....
+%     *obj = cdev_pager_allocate(vmh, OBJT_DEVICE, 
+%              &contigmem_cdev_pager_ops,size, nprot, 
+%              *offset, curthread->td_ucred);
+
+%     return 0;
+%   }
+%   \end{lstlisting}
+
+\subsubsection{Sample memory allocator design}
+
+\begin{lstlisting}[linewidth=\columnwidth,breaklines=true,language=C, caption=Contigmem driver mmap , label=MallocSample]
+  #define FILENAME "/dev/contigmem"
+  void *ptr;
+  int MallocCounter;
+
+  size_t sizeUsed;
+
+  ...
+
+  INITAlloc(void) {
+
+  size_t sz;
+  sz = 100000000;
+
+  int fd = open(FILENAME, O_RDWR, 0600);
+
+   if (fd < 0) {
+       perror("open");
+       exit(EXIT_FAILURE);
+   }
+
+   off_t offset = 0; // offset to seek to.
+
+   if (ftruncate(fd, sz) < 0) {
+       perror("ftruncate");
+       close(fd);
+       exit(EXIT_FAILURE);
+   }
+
+   ptr = mmap(NULL, sz,
+   PROT_READ|PROT_WRITE, MAP_SHARED,fd,0);
+
+  // Added error handling
+   if(ptr == MAP_FAILED)
+   {
+       perror("mmap");
+       exit(EXIT_FAILURE);
+   }
+   MallocCounter = (int)sz;
+   }
+
+   void* malloc(size_t sz)
+   {
+  sz = __builtin_align_up(sz, _Alignof(max_align_t));
+
+  // printf("%d \n", sz);
+  // printf("%d Malloc counter\n", MallocCounter);
+
+  MallocCounter -= sz;
+  void *ptrLink = &ptr[MallocCounter];
+  ptrLink = cheri_setbounds(ptrLink, sz);
+
+  return ptrLink;
+
+  }
+
+  void FREECHERI(void *ptr) {
+
+  // get length of free from bounds
+  // in the pointer
+  int len = cheri_getlen(ptr);
+
+  munmap(ptr, len);
+}
+
+\end{lstlisting}
+
+The code snippet.;
+ below shows a sample memory allocator
+which is a really simple implementation that initially 
+in the example allocates 1GB of memory using the mmap call which calls 
+the mmap function from /dev/contigmem driver. This ensures memory allocated to the physically
+contiguous memory allocated in the contigmem\_load() function using the contigmem\_mmap\_single()
+function call in the kernel module, uses malloc 
+and free to allocate within this memory chuck. The consideration of this is to ensure that a C program needs minor changes to use the benefit
+using physically contiguous memory with bounds within a segment of memory.
 
 \section{Related work}
-
-\section{Summary}
-
-% \section{Introduction}
-% ACM's consolidated article template, introduced in 2017, provides a
-% consistent \LaTeX\ style for use across ACM publications, and
-% incorporates accessibility and metadata-extraction functionality
-% necessary for future Digital Library endeavors. Numerous ACM and
-% SIG-specific \LaTeX\ templates have been examined, and their unique
-% features incorporated into this single new template.
-
-% If you are new to publishing with ACM, this document is a valuable
-% guide to the process of preparing your work for publication. If you
-% have published with ACM before, this document provides insight and
-% instruction into more recent changes to the article template.
-
-% The ``\verb|acmart|'' document class can be used to prepare articles
-% for any ACM publication --- conference or journal, and for any stage
-% of publication, from review to final ``camera-ready'' copy, to the
-% author's own version, with {\itshape very} few changes to the source.
+\subsection{Huge Pages}
+% This is used to map a very large region of memory to a 
+% single entry. This small/large region of memory is physically
+% contiguous. Most implementations of huge pages \cite{panwar_hawkeye_2019} are size
+% aligned, For example for the x86 architecture the huge pages 
+% size are 4KB, 2MB and 1GB pages. 
+Increasing TLB reach can be achieved by using larger page sizes, such as huge pages\cite{panwarhawkeye2019}, which are common in modern computer systems. 
+The x86-64 architecture supports huge pages of 2 MB and 1 GB, backed by OS mechanisms like Transparent Huge Pages (THP) 
+and HugeTLBFS in Linux. However, available page sizes in x86-64 are limited, leading to internal fragmentation issues. 
+For instance, allocating 1 MB with 4 KB base pages requires 256 PTEs, but using a 2 MB huge page would waste 
+half of the memory space. Some architectures offer more page size choices, such as Intel Itanium, which 
+allows different areas of the address space to have their own page sizes. Itanium uses a hash page table to organize huge 
+pages, but without significant changes to the conventional page table, it only helps reduce page walk overheads. 
+HP Tunable Base Page Size permits the OS to adjust the base page size, but still faces internal fragmentation problems, 
+with HP recommending a base page size of no more than 16 KB. Shadow Superpage introduces a new translation level 
+in the memory controller to merge non-contiguous physical pages into a huge page in a shadow memory space, extending 
+TLB coverage. However, this approach requires all memory traffic to be translated again in the memory controller, 
+resulting in additional latency for memory accesses.
+
+\subsection{Segment}
+% A segment\cite{basu_efficient_nodate} can be viewed as mapping between contiguous virtual
+% memory and contiguous physical memory. The property of a 
+% segment allows it to be larger than a page. Direct Segment allows the user to set a single segment
+% for an application. Two registers are added to mark the start
+% and end of the segment. Any virtual address within this region
+% can be translated by adding the fixed offset between the virtual
+% and physical address.
+Early processors often used segments to manage virtual memory, where a segment essentially mapped contiguous 
+virtual memory to contiguous physical memory. Unlike pages, which are relatively small, segments can be much 
+larger, offering the potential for more efficient memory management in certain scenarios. 
+This concept of segmentation has seen a resurgence in some modern approaches that aim to enhance 
+translation coverage by designating specific areas in the virtual address space.
+
+% Alternate segment technique
+% - JayneelGandhi,ArkapravaBasu,MarkD.Hill,andMichaelM.Swift.2014.Efficientmemoryvirtualization:Reducing
+This method allows programmers to explicitly define 
+a single segment for applications requiring significant memory. It introduces two new 
+registers to the system, which indicate the start and end of this segment. 
+Virtual addresses within this segment are translated by calculating 
+the offset from the virtual start address and applying this offset to the 
+physical start address. This straightforward method simplifies the translation 
+process for large memory areas but requires significant modifications to the 
+source code of applications.
+
+\subsection{Range Memory Mapping (RMM):}
+% RMM\cite{karakostas_redundant_2015} introduces the concept of adding an additional range table.
+% For large allocations RMM eagerly allocates contiguous physical pages.
+% The following allocations creates large memory ranges that are
+% both virtually and physically contiguous. RMM builds on the concept
+% of Direct segment by adding offset to translate a virtual address 
+% to physical address. RMM compares address with range boundaries 
+% to decide which range it belongs to. RMM queries the range table 
+% ofter an L1 TLB miss.
+Redundant Memory Mappings (RMM)\cite{karakostasredundant2015} enhance memory management by introducing an additional range table 
+that pre-allocates contiguous physical pages for large memory allocations, creating ranges that 
+are both virtually and physically contiguous. This approach simplifies address translation 
+within these ranges by adding an offset, similar to Direct Segment, but RMM supports multiple 
+ranges and operates transparently to programmers, requiring no source code modifications. 
+The range table, separate from the conventional page table, holds the mappings for these 
+large allocations. To determine which range an address belongs to, RMM compares the address 
+against all range boundaries, a process that is computationally expensive and therefore performed 
+only after an L1 TLB miss. To optimize this, RMM uses a range TLB (RTLB) to quickly identify 
+if an address falls within any pre-allocated range, facilitating efficient translation and 
+reducing overhead. Range mapping works alongside the paging system by generating TLB entries on 
+TLB misses and still performing TLB lookups for each virtual address translation. 
+Unlike traditional segmentation mechanisms, range mapping activates a range lookaside 
+buffer (RTLB) located with the last level TLB upon a miss. The hardware TLB miss 
+handler then searches the RTLB for the miss address and, if found, generates a new 
+TLB entry with the physical address derived from the base virtual address and 
+range offset, along with permission bits. If the RTLB also misses, the system 
+defaults to a standard page walk while a range table walker simultaneously 
+loads the range into the RTLB in the background, avoiding delays in memory operations. 
+The RTLB, functioning as a fully associative search structure, ensures 
+that most last level TLB misses are handled efficiently by range mapping, 
+reducing the need for costly page table walks.
+
+\subsection{CHERI}
+CHERI (Capability Hardware Enhanced RISC Instructions) extends conventional processor
+Instruction-Set Architectures (ISAs) with architectural capabilities to enable fine-grained
+memory protection and highly scalable software compartmentalization. CHERI is a hybrid 
+capability architecture that can combine capabilities with conventional MMU(i.e Memory Management
+ Unit) based systems. The contribution of the following project include: 
+\begin{itemize}
+  \item ISA changes to introduce architecture capabilities.
+  \item New microarchitecture proving that capabilities can be implemented efficiently 
+        in hardware. Support for efficient tagged memory to protect capabilities and
+        compress capabilities to reduce memory overhead.   
+  \item Newly designed software construction model for that uses capability to provide
+        fine grain memory protection and scalable software compartmentalization.  
+  \item Language and Compiler extension to use capabilities for C and C++.
+  \item OS extensions to use (and support application use of) fine-grained memory protection
+        (spatial, referential, and (non-stack) temporal memory safety) and abstraction extensions
+        to support scalable software compartmentalization. 
+\end{itemize}
+
+\subsection{Future work}
+The current experimental setup on the ARM Morello board is constrained by the requirement that all memory reads must 
+pass through the Translation Lookaside Buffer (TLB) for address translation. This necessitates frequent TLB lookups, potentially 
+leading to performance bottlenecks. The planned future work aims to address this by leveraging CHERI 
+(Capability Hardware Enhanced RISC Instructions) extensions on the RISC-V architecture, specifically using the 
+Tooba implementation.
+
+\subsubsection{Storing Offsets Directly on Pointers}
+In the current ARM Morello setup, address translations rely on the TLB.
+The future approach on RISC-V Tooba involves storing the offset directly within the pointer.
+This is possible due to CHERI's capability model, which supports fine-grained memory protection and can encode bounds within pointers.
+Utilizing Bounds in CHERI for Block-Based Allocation:
+
+CHERI capabilities allow pointers to carry metadata about memory bounds, providing hardware-enforced memory safety.
+By encoding the offset and bounds within the pointer, the system can directly access memory without needing intermediate translations via the TLB.
+This enables the implementation of a block-based allocator that can efficiently manage memory allocations and deallocations within defined bounds.
+Bypassing the TLB in RISC-V Tooba.
+\subsubsection{Hardware Modifications:}
+The Bluespec design of the RISC-V processor will be modified to allow certain memory operations to bypass the TLB.
+This means that when a pointer with encoded offset and bounds is used, the system can directly compute the physical address from the capability information.
+This modification reduces the dependency on the TLB, decreasing latency and improving performance, especially for frequent memory operations.
+Transition to a Single-Address-Space Operating System (SASOS)\cite{esswoodcheriosnodate}.
+\subsubsection{Concept of SASOS:}
+In traditional operating systems, there is a clear separation between user space and kernel space. This separation is enforced by memory protection mechanisms and address translation through the TLB.
+In a Single-Address-Space Operating System, this distinction is removed. Both user applications and the kernel share the same contiguous address space.
+\subsubsection{Advantages of SASOS with CHERI:}
+% Rewrite this bit
+\begin{itemize}
+  \item Simplified Memory Management : Without the need to switch between user and kernel spaces, memory management becomes simpler and more efficient.
+The kernel allocator can be the same as the user space allocator, operating on a single, contiguous chunk of memory.
+  \item Unified Allocator: The unified memory allocator can efficiently manage memory for both kernel and user applications, leveraging CHERI's capability-based protection to prevent unauthorized access.
+This reduces overhead and potential fragmentation issues associated with maintaining separate memory spaces.
+\end{itemize}
+
+\section{Conclusion}  %Title of the Conclusion
+This paper addresses the growing disparity between application workloads and the capacity of Translation Lookaside Buffers (TLBs). 
+To mitigate this gap, it proposes leveraging physically contiguous memory to optimize TLB utilization. Additionally, 
+the report explores advancements in system security, particularly through the Capability Hardware Enhanced RISC Instructions (CHERI) 
+architecture. CHERI's capability-based addressing enhances system security by associating capabilities with memory pointers, 
+restricting access to memory regions, and thus protecting against various security threats. Importantly, these mechanisms 
+can also improve the efficiency of memory allocators by managing memory resources while ensuring robust security measures.
+\newline
+
+This paper highlights the constant pursuit of optimal performance in computing, emphasizing the importance of 
+efficient memory management. TLBs are crucial in expediting memory access by storing recently accessed memory translations. 
+However, as applications grow in size and complexity, TLB capacity often becomes a bottleneck. One innovative solution 
+is the use of huge pages, which allocate memory in larger chunks, thereby reducing the number of TLB entries required 
+and potentially enhancing overall system performance. Advancements in hardware-level security, such as CHERI's 
+capability-based addressing, offer additional performance enhancement opportunities by tightly controlling memory 
+access and accelerating memory management operations. Integrating huge pages into memory management strategies 
+alongside CHERI's capability-based addressing can optimize TLB utilization and leverage security features for 
+significant performance improvements.
+\newline
+% The future work section outlines the planned research timeline, focusing on the development and evaluation of FAT-pointer-based 
+% range addresses. Key milestones include the initial development phase in July 2024, followed by integration with the RISC-V architecture 
+% from August to September 2024. Detailed testing and evaluation are scheduled from October 2024 to February 2025, with an extension 
+% of the implementation to uni-kernels planned from March to May 2025. Finalization and optimization of the approach are expected 
+% from June to September 2025, culminating in a comprehensive evaluation and documentation of the results from January to September 2026.
+% \newline
+
+This paper aims to demonstrate how leveraging physically contiguous memory and advanced security architectures like CHERI can 
+enhance memory management efficiency while ensuring robust security measures. These advancements ultimately contribute to 
+improved system performance, addressing the challenges posed by the increasing complexity and size of modern application workloads.
+
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{paperReferences}
 
@@
 % \begin{verbatim}
-% \documentclass[acmsmall,screen,review]{acmart}
+% \documentclass[sigconf,authordraft]{acmart}
 % \end{verbatim}
@@
 % in the example below.
-% \begin{figure}[h]
-%   \centering
-%   \includegraphics[width=\linewidth]{sample-franklin}
-%   \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-%     Ewing, Inc. [Public domain], via Wikimedia
-%     Commons. (\url{https://goo.gl/VLCRBB}).}
-%   \Description{A woman and a girl in white dresses sit in an open car.}
-% \end{figure}
+% % \begin{figure}[h]
+% %   \centering
+% %   \includegraphics[width=\linewidth]{sample-franklin}
+% %   \caption{1907 Franklin Model D roadster. Photograph by Harris \&
+% %     Ewing, Inc. [Public domain], via Wikimedia
+% %     Commons. (\url{https://goo.gl/VLCRBB}).}
+% %   \Description{A woman and a girl in white dresses sit in an open car.}
+% % \end{figure}
 
@@
 % \verb|\maketitle| command:
-% \begin{verbatim}
-%   \begin{teaserfigure}
-%     \includegraphics[width=\textwidth]{sampleteaser}
-%     \caption{figure caption}
-%     \Description{figure description}
-%   \end{teaserfigure}
-% \end{verbatim}
+% % \begin{verbatim}
+% %   \begin{teaserfigure}
+% %     \includegraphics[width=\textwidth]{sampleteaser}
+% %     \caption{figure caption}
+% %     \Description{figure description}
+% %   \end{teaserfigure}
+% % \end{verbatim}
 
@@
 
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
+% %%
+% %% The acknowledgments section is defined using the "acks" environment
+% %% (and NOT an unnumbered section). This ensures the proper
+% %% identification of the section in the article metadata, and the
+% %% consistent spelling of the heading.
 % \begin{acks}
@@
 
-\begin{acks}
-  To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{references}
-
+% %%
+% %% The next two lines define the bibliography style to be used, and
+% %% the bibliography file.
+% \bibliographystyle{ACM-Reference-Format}
+% \bibliography{sample-base}
+
+% %%
+% %% If your work has an appendix, this is the place to put it.
 % \appendix
@@
 %%
-%% End of file `sample-acmsmall-submission.tex'.
+%% End of file `sample-sigconf-authordraft.tex'.
